---
title: "Machine Learning Algorithm"
author: "RR"
date: "16 dicembre 2016"
output: html_document
---

```{r Load R libraries}
library(plyr)
library(DMwR)
library(ggplot2)
library(caret)
library(stringr)
options( java.parameters = "-Xmx12g" )
library( "RWeka" )
library(rJava)
# Enable parallel execution if available
if(.Platform$OS.type == "unix"){
  library(doMC)
  library(parallel)
  registerDoMC(detectCores())
}
if(.Platform$OS.type == "windows"){
  library(foreach)
  library(doParallel)
  # cl<-makeCluster(8)
  #registerDoParallel(detectCores())
    registerDoParallel(4)
}
```


```{r read package csv jgit}
knitr::opts_chunk$set(cache=TRUE)#attivata la cache del markdown
# to.timestamp <- function(d) as.POSIXct(d, format="%Y-%m-%dT%H:%M:%S")
to.timestamp.fromint <- function(d) as.POSIXct(d,origin = "1970-01-01", tz = "GMT")
# library(data.table)
# pkg.merged<-fread("cache/jgit/package_merged.csv")
# pkg.merged[,.(commit_time=to.timestamp.fromint(pkg.merged$commit_time))]
# head(pkg.merged)

pkg.merged.df <- read.csv("cache/jgit/package_merged.dev.csv",
                          head=TRUE,
                          sep=",")
pkg.merged.df$commit_time<-to.timestamp.fromint(pkg.merged.df$commit_time)
# Add missing column UD copying the number of correlated packages. It will by transformed to a factor below
    pkg.merged.df$UD <- pkg.merged.df$UDnumCorrelatedPackage
    pkg.merged.df <- subset(pkg.merged.df, select = -c(minRatio.out, minRatio.in, UDminInstabilityCorrelatedPackage, HLminFanIn, HLminFanOut, HLminTD,
    maxRatio.out, maxRatio.in, UDmaxInstabilityCorrelatedPackage, HLmaxFanIn, HLmaxFanOut, HLmaxTD,
    meanRatio.out, meanRatio.in, UDmeanInstabilityCorrelatedPackage, UDsdInstabilityCorrelatedPackage,
    HLmeanFanIn, HLsdFanIn, HLmeanFanOut, HLsdFanOut, HLmeanTD, HLsdTD, InstabilityUnstableDependenciesPackage,RMA,RMI,CE,CA,RMD))
```

```{r group data by year-month-day}
# library(plyr)

pkg.merged.df$commit_date <- factor(strftime(pkg.merged.df$commit_time, "%Y-%m"))

pkg.merged.df <- ddply(pkg.merged.df[setdiff(names(pkg.merged.df),c("version", "commit_time"))],
                       .(package, commit_date),
                       function(slice) {
                           slice.cols <- setdiff(names(slice), c("package", "commit_date", "author", "mail"))
  cbind(colwise(min)(slice[, slice.cols[grep("min", slice.cols)]]),
        colwise(max)(slice[, slice.cols[grep("max", slice.cols)]]),
        colwise(mean)(slice[, slice.cols[grep("(mean|sd)", slice.cols)]]),
        colwise(sum)(slice[, slice.cols[grep("(min|max|mean|sd)", slice.cols, invert = TRUE)]])
  )
}, .progress = "text")
```


```{r Lagging package metrics}
lag.df <- function(df, lags, colnames = names(df)) {
  # this can yield unexpected errors if nrow(df) <= lags
  if(nrow(df) > lags) {
    lagged <- df
    for(i in 1:lags) {
        attached <- df[(1+i):nrow(df), colnames]
        names(attached) <- paste0(names(attached), "-", i)
        lagged <- cbind(lagged[1:(nrow(df)-i), ], attached, row.names = NULL)
    }
    return(lagged)
  } else {
    df[0:0, ]
  }
}
lag.dt <- function(dt, lags, colnames = names(dt)) {
  # this can yield unexpected errors if nrow(df) <= lags  
  lagged <- dt[,shift(.SD,n=1:lags,give.names = TRUE), colnames]
    # for(i in 1:lags) {
       # nm1<-dt[, colnames]
       # nm2 <- paste( nm1,"", sep="-")
       # lagged <-dt[, (nm2) :=  shift(.SD,1:5,give.names = TRUE), .SDcols=nm1]
    # }
    return(lagged)
}
```

#Lag packages value and use caret to perform machine learning
```{r lag package dataset}
# setkey(pkg.merged,"version", "commit_time","package")
# pkg.lagged <- lag.dt(pkg.merged,
#                      5,
#                      setdiff(names(pkg.merged), c("version", "commit_time","package")))
pkg.merged.df <- subset(pkg.merged.df, select=-c(minCommit.out, maxCommit.out, meanCommit.out, minCommit.in, maxCommit.in, meanCommit.in))#, minRatio.out, maxRatio.out, meanRatio.out, minRatio.in, maxRatio.in, meanRatio.in))

pkg.lagged <- ddply(pkg.merged.df, .(package), function(pkg) {
  sorted <- pkg[order(pkg[["commit_date"]], decreasing = TRUE), ]
  lag.df(sorted, 12, colnames = setdiff(names(sorted), c("package", "commit_date")))
}, .progress = "text")
```

Please before use caret install all the dependencies and the suggested ones (are more than 400)
install.packages("caret", dependencies = c("Depends", "Suggests"))
follow istruction at <https://cran.r-project.org/web/packages/caret/vignettes/caret.pdf/>

```{r cv test star pkg}
# library(plyr)#colwise
# library(ggplot2)
# library(caret)
shapes <- c("star", "circle", "tiny", "clique", "chain")
targets <- c(shapes, "CD", "UD", "HL", "IXPD")
pkg.dataset <- subset(pkg.lagged, select=-c(commit_date, package))
head(pkg.dataset)
tfcutter <- colwise(cut, breaks = c(0,1,.Machine$integer.max), labels = c(0, 1), right = FALSE, ordered_result = TRUE)
pkg.dataset <- cbind(tfcutter(pkg.dataset[targets]), pkg.dataset[setdiff(names(pkg.dataset), targets)])
head(pkg.dataset)

# Remove columns with near-zero variance
pkg.dataset.nzv <- pkg.dataset[, -nearZeroVar(pkg.dataset)]

fitControl <- trainControl(## 10-fold CV
                           method = "repeatedcv",
                           number = 10,
                           ## repeated ten times
                           repeats = 10,
                           savePredictions = TRUE,
                           verboseIter = TRUE,
                           sampling = "down")
# Enable parallel execution if available
# if(.Platform$OS.type == "unix"){
#   library(doMC)
#   library(parallel)
#   registerDoMC(detectCores())
# }
# if(.Platform$OS.type == "windows"){
#   library(foreach)
#   library(doParallel)
#   # cl<-makeCluster(8)
#   registerDoParallel(detectCores())
# }

# define a function to encapsulate the training procedure
runCV <- function(lagged, .models, .shapes, .outfilePrefix = "") {
  # Generate all combinations of targets and models to test
  experiments <- expand.grid(shape = .shapes, model = .models)
  adply(experiments, .margins = 1, function(experiment) {
    currentShape <- paste(experiment[1, "shape"])
    currentModel <- paste(experiment[1, "model"])
    
    if (currentShape %in% names(lagged)) {
      # Keep only lagged columns in the dataset, plus the class
      lagged.train <- cbind(lagged[c(currentShape)],
                            lagged[grep("-", names(lagged))])
      print(paste("Model:", currentModel))
      print(names(lagged.train))
      fit <- train(as.formula(paste(currentShape, "~ .")),
                   data = lagged.train,
                   method = currentModel,
                   trControl = fitControl)
      cm <- confusionMatrix(confusionMatrix(fit, norm = "none")$table,
                            positive = "1",
                            mode = "prec_recall")
      cm.df <- data.frame(as.list(cm$overall), as.list(cm$byClass))
        write.csv(cm.df, paste0(.outfilePrefix, "cm-", currentShape, "-", currentModel, ".csv"))
		saveRDS(fit, paste0(.outfilePrefix, "model-", currentShape, "-", currentModel, ".rds"))
      cm.df
    } else {
      data.frame()
    }
  })
}

    fitControl.smote <- trainControl(## 10-fold CV
                           method = "repeatedcv",
                           number = 10,
   ## repeated ten times
                           repeats = 10,
                           savePredictions = TRUE,
                           verboseIter = TRUE,
                           sampling = "smote")
    runCV.smote <- function(lagged, .models, .shapes, .outfilePrefix = "") {
        # Generate all combinations of targets and models to test
        experiments <- expand.grid(shape = .shapes, model = .models)
        adply(experiments, .margins = 1, function(experiment) {
            currentShape <- paste(experiment[1, "shape"])
            currentModel <- paste(experiment[1, "model"])

            if (currentShape %in% names(lagged)) {
                # Keep only lagged columns in the dataset, plus the class
                lagged.train <- cbind(lagged[c(currentShape)],
                            lagged[grep("-", names(lagged))])
                print(paste("Model:", currentModel))
                print(names(lagged.train))
                fit <- train(as.formula(paste(currentShape, "~ .")),
                   data = lagged.train,
                   method = currentModel,
                   trControl = fitControl.smote)
                cm <- confusionMatrix(confusionMatrix(fit, norm = "none")$table,
                            positive = "1",
                            mode = "prec_recall")
                cm.df <- data.frame(as.list(cm$overall), as.list(cm$byClass))
                write.csv(cm.df, paste0(.outfilePrefix, "cm-", currentShape, "-", currentModel, ".csv"))
				saveRDS(fit, paste0(.outfilePrefix, "model-", currentShape, "-", currentModel, ".rds"))
                cm.df
            } else {
                data.frame()
            }
        })
    }



```

[1] "Model: nb"
 [1] "star"                 "max.file.changed-1"   "numjavafile-1"        "nummail-1"            "sum.added.total-1"    "sum.removed.total-1"  "sum.added.file-1"    
 [8] "sum.removed.file-1"   "CD-1"                 "max.file.changed-2"   "numjavafile-2"        "nummail-2"            "sum.added.total-2"    "sum.removed.total-2" 
[15] "sum.added.file-2"     "CD-2"                 "max.file.changed-3"   "numjavafile-3"        "nummail-3"            "sum.added.total-3"    "sum.removed.total-3" 
[22] "sum.added.file-3"     "sum.removed.file-3"   "CD-3"                 "max.file.changed-4"   "numjavafile-4"        "nummail-4"            "sum.added.total-4"   
[29] "sum.removed.total-4"  "sum.added.file-4"     "CD-4"                 "max.file.changed-5"   "numjavafile-5"        "nummail-5"            "sum.added.total-5"   
[36] "sum.removed.total-5"  "sum.added.file-5"     "CD-5"                 "max.file.changed-6"   "numjavafile-6"        "nummail-6"            "sum.added.total-6"   
[43] "sum.removed.total-6"  "sum.added.file-6"     "sum.removed.file-6"   "CD-6"                 "max.file.changed-7"   "numjavafile-7"        "nummail-7"           
[50] "sum.added.total-7"    "sum.removed.total-7"  "sum.added.file-7"     "sum.removed.file-7"   "CD-7"                 "max.file.changed-8"   "numjavafile-8"       
[57] "nummail-8"            "sum.added.total-8"    "sum.removed.total-8"  "sum.added.file-8"     "sum.removed.file-8"   "CD-8"                 "max.file.changed-9"  
[64] "numjavafile-9"        "nummail-9"            "sum.added.total-9"    "sum.removed.total-9"  "sum.added.file-9"     "sum.removed.file-9"   "CD-9"                
[71] "max.file.changed-10"  "numjavafile-10"       "nummail-10"           "sum.added.total-10"   "sum.removed.total-10" "sum.added.file-10"    "sum.removed.file-10" 
[78] "CD-10"                "max.file.changed-11"  "numjavafile-11"       "nummail-11"           "sum.added.total-11"   "sum.removed.total-11" "sum.added.file-11"   
[85] "sum.removed.file-11"  "CD-11"                "max.file.changed-12"  "numjavafile-12"       "nummail-12"           "sum.added.total-12"   "sum.removed.total-12"
[92] "sum.added.file-12"    "sum.removed.file-12"  "CD-12"               
Aggregating results
Selecting tuning parameters
Fitting fL = 0, usekernel = FALSE, adjust = 1 on full training set
[1] "Model: nb"
 [1] "circle"               "max.file.changed-1"   "numjavafile-1"        "nummail-1"            "sum.added.total-1"    "sum.removed.total-1"  "sum.added.file-1"    
 [8] "sum.removed.file-1"   "CD-1"                 "max.file.changed-2"   "numjavafile-2"        "nummail-2"            "sum.added.total-2"    "sum.removed.total-2" 
[15] "sum.added.file-2"     "CD-2"                 "max.file.changed-3"   "numjavafile-3"        "nummail-3"            "sum.added.total-3"    "sum.removed.total-3" 
[22] "sum.added.file-3"     "sum.removed.file-3"   "CD-3"                 "max.file.changed-4"   "numjavafile-4"        "nummail-4"            "sum.added.total-4"   
[29] "sum.removed.total-4"  "sum.added.file-4"     "CD-4"                 "max.file.changed-5"   "numjavafile-5"        "nummail-5"            "sum.added.total-5"   
[36] "sum.removed.total-5"  "sum.added.file-5"     "CD-5"                 "max.file.changed-6"   "numjavafile-6"        "nummail-6"            "sum.added.total-6"   
[43] "sum.removed.total-6"  "sum.added.file-6"     "sum.removed.file-6"   "CD-6"                 "max.file.changed-7"   "numjavafile-7"        "nummail-7"           
[50] "sum.added.total-7"    "sum.removed.total-7"  "sum.added.file-7"     "sum.removed.file-7"   "CD-7"                 "max.file.changed-8"   "numjavafile-8"       
[57] "nummail-8"            "sum.added.total-8"    "sum.removed.total-8"  "sum.added.file-8"     "sum.removed.file-8"   "CD-8"                 "max.file.changed-9"  
[64] "numjavafile-9"        "nummail-9"            "sum.added.total-9"    "sum.removed.total-9"  "sum.added.file-9"     "sum.removed.file-9"   "CD-9"                
[71] "max.file.changed-10"  "numjavafile-10"       "nummail-10"           "sum.added.total-10"   "sum.removed.total-10" "sum.added.file-10"    "sum.removed.file-10" 
[78] "CD-10"                "max.file.changed-11"  "numjavafile-11"       "nummail-11"           "sum.added.total-11"   "sum.removed.total-11" "sum.added.file-11"   
[85] "sum.removed.file-11"  "CD-11"                "max.file.changed-12"  "numjavafile-12"       "nummail-12"           "sum.added.total-12"   "sum.removed.total-12"
[92] "sum.added.file-12"    "sum.removed.file-12"  "CD-12"               
Aggregating results
Selecting tuning parameters
Fitting fL = 0, usekernel = TRUE, adjust = 1 on full training set
[1] "Model: nb"
 [1] "clique"               "max.file.changed-1"   "numjavafile-1"        "nummail-1"            "sum.added.total-1"    "sum.removed.total-1"  "sum.added.file-1"    
 [8] "sum.removed.file-1"   "CD-1"                 "max.file.changed-2"   "numjavafile-2"        "nummail-2"            "sum.added.total-2"    "sum.removed.total-2" 
[15] "sum.added.file-2"     "CD-2"                 "max.file.changed-3"   "numjavafile-3"        "nummail-3"            "sum.added.total-3"    "sum.removed.total-3" 
[22] "sum.added.file-3"     "sum.removed.file-3"   "CD-3"                 "max.file.changed-4"   "numjavafile-4"        "nummail-4"            "sum.added.total-4"   
[29] "sum.removed.total-4"  "sum.added.file-4"     "CD-4"                 "max.file.changed-5"   "numjavafile-5"        "nummail-5"            "sum.added.total-5"   
[36] "sum.removed.total-5"  "sum.added.file-5"     "CD-5"                 "max.file.changed-6"   "numjavafile-6"        "nummail-6"            "sum.added.total-6"   
[43] "sum.removed.total-6"  "sum.added.file-6"     "sum.removed.file-6"   "CD-6"                 "max.file.changed-7"   "numjavafile-7"        "nummail-7"           
[50] "sum.added.total-7"    "sum.removed.total-7"  "sum.added.file-7"     "sum.removed.file-7"   "CD-7"                 "max.file.changed-8"   "numjavafile-8"       
[57] "nummail-8"            "sum.added.total-8"    "sum.removed.total-8"  "sum.added.file-8"     "sum.removed.file-8"   "CD-8"                 "max.file.changed-9"  
[64] "numjavafile-9"        "nummail-9"            "sum.added.total-9"    "sum.removed.total-9"  "sum.added.file-9"     "sum.removed.file-9"   "CD-9"                
[71] "max.file.changed-10"  "numjavafile-10"       "nummail-10"           "sum.added.total-10"   "sum.removed.total-10" "sum.added.file-10"    "sum.removed.file-10" 
[78] "CD-10"                "max.file.changed-11"  "numjavafile-11"       "nummail-11"           "sum.added.total-11"   "sum.removed.total-11" "sum.added.file-11"   
[85] "sum.removed.file-11"  "CD-11"                "max.file.changed-12"  "numjavafile-12"       "nummail-12"           "sum.added.total-12"   "sum.removed.total-12"
[92] "sum.added.file-12"    "sum.removed.file-12"  "CD-12"               
Aggregating results
Selecting tuning parameters
Fitting fL = 0, usekernel = TRUE, adjust = 1 on full training set
[1] "Model: nb"
 [1] "chain"                "max.file.changed-1"   "numjavafile-1"        "nummail-1"            "sum.added.total-1"    "sum.removed.total-1"  "sum.added.file-1"    
 [8] "sum.removed.file-1"   "CD-1"                 "max.file.changed-2"   "numjavafile-2"        "nummail-2"            "sum.added.total-2"    "sum.removed.total-2" 
[15] "sum.added.file-2"     "CD-2"                 "max.file.changed-3"   "numjavafile-3"        "nummail-3"            "sum.added.total-3"    "sum.removed.total-3" 
[22] "sum.added.file-3"     "sum.removed.file-3"   "CD-3"                 "max.file.changed-4"   "numjavafile-4"        "nummail-4"            "sum.added.total-4"   
[29] "sum.removed.total-4"  "sum.added.file-4"     "CD-4"                 "max.file.changed-5"   "numjavafile-5"        "nummail-5"            "sum.added.total-5"   
[36] "sum.removed.total-5"  "sum.added.file-5"     "CD-5"                 "max.file.changed-6"   "numjavafile-6"        "nummail-6"            "sum.added.total-6"   
[43] "sum.removed.total-6"  "sum.added.file-6"     "sum.removed.file-6"   "CD-6"                 "max.file.changed-7"   "numjavafile-7"        "nummail-7"           
[50] "sum.added.total-7"    "sum.removed.total-7"  "sum.added.file-7"     "sum.removed.file-7"   "CD-7"                 "max.file.changed-8"   "numjavafile-8"       
[57] "nummail-8"            "sum.added.total-8"    "sum.removed.total-8"  "sum.added.file-8"     "sum.removed.file-8"   "CD-8"                 "max.file.changed-9"  
[64] "numjavafile-9"        "nummail-9"            "sum.added.total-9"    "sum.removed.total-9"  "sum.added.file-9"     "sum.removed.file-9"   "CD-9"                
[71] "max.file.changed-10"  "numjavafile-10"       "nummail-10"           "sum.added.total-10"   "sum.removed.total-10" "sum.added.file-10"    "sum.removed.file-10" 
[78] "CD-10"                "max.file.changed-11"  "numjavafile-11"       "nummail-11"           "sum.added.total-11"   "sum.removed.total-11" "sum.added.file-11"   
[85] "sum.removed.file-11"  "CD-11"                "max.file.changed-12"  "numjavafile-12"       "nummail-12"           "sum.added.total-12"   "sum.removed.total-12"
[92] "sum.added.file-12"    "sum.removed.file-12"  "CD-12"               
Aggregating results
Selecting tuning parameters
Fitting fL = 0, usekernel = TRUE, adjust = 1 on full training set
[1] "Model: nb"
 [1] "CD"                   "max.file.changed-1"   "numjavafile-1"        "nummail-1"            "sum.added.total-1"    "sum.removed.total-1"  "sum.added.file-1"    
 [8] "sum.removed.file-1"   "CD-1"                 "max.file.changed-2"   "numjavafile-2"        "nummail-2"            "sum.added.total-2"    "sum.removed.total-2" 
[15] "sum.added.file-2"     "CD-2"                 "max.file.changed-3"   "numjavafile-3"        "nummail-3"            "sum.added.total-3"    "sum.removed.total-3" 
[22] "sum.added.file-3"     "sum.removed.file-3"   "CD-3"                 "max.file.changed-4"   "numjavafile-4"        "nummail-4"            "sum.added.total-4"   
[29] "sum.removed.total-4"  "sum.added.file-4"     "CD-4"                 "max.file.changed-5"   "numjavafile-5"        "nummail-5"            "sum.added.total-5"   
[36] "sum.removed.total-5"  "sum.added.file-5"     "CD-5"                 "max.file.changed-6"   "numjavafile-6"        "nummail-6"            "sum.added.total-6"   
[43] "sum.removed.total-6"  "sum.added.file-6"     "sum.removed.file-6"   "CD-6"                 "max.file.changed-7"   "numjavafile-7"        "nummail-7"           
[50] "sum.added.total-7"    "sum.removed.total-7"  "sum.added.file-7"     "sum.removed.file-7"   "CD-7"                 "max.file.changed-8"   "numjavafile-8"       
[57] "nummail-8"            "sum.added.total-8"    "sum.removed.total-8"  "sum.added.file-8"     "sum.removed.file-8"   "CD-8"                 "max.file.changed-9"  
[64] "numjavafile-9"        "nummail-9"            "sum.added.total-9"    "sum.removed.total-9"  "sum.added.file-9"     "sum.removed.file-9"   "CD-9"                
[71] "max.file.changed-10"  "numjavafile-10"       "nummail-10"           "sum.added.total-10"   "sum.removed.total-10" "sum.added.file-10"    "sum.removed.file-10" 
[78] "CD-10"                "max.file.changed-11"  "numjavafile-11"       "nummail-11"           "sum.added.total-11"   "sum.removed.total-11" "sum.added.file-11"   
[85] "sum.removed.file-11"  "CD-11"                "max.file.changed-12"  "numjavafile-12"       "nummail-12"           "sum.added.total-12"   "sum.removed.total-12"
[92] "sum.added.file-12"    "sum.removed.file-12"  "CD-12"               
Aggregating results
Selecting tuning parameters
Fitting fL = 0, usekernel = FALSE, adjust = 1 on full training set
[1] "Model: nb"
 [1] "UD"                   "max.file.changed-1"   "numjavafile-1"        "nummail-1"            "sum.added.total-1"    "sum.removed.total-1"  "sum.added.file-1"    
 [8] "sum.removed.file-1"   "CD-1"                 "max.file.changed-2"   "numjavafile-2"        "nummail-2"            "sum.added.total-2"    "sum.removed.total-2" 
[15] "sum.added.file-2"     "CD-2"                 "max.file.changed-3"   "numjavafile-3"        "nummail-3"            "sum.added.total-3"    "sum.removed.total-3" 
[22] "sum.added.file-3"     "sum.removed.file-3"   "CD-3"                 "max.file.changed-4"   "numjavafile-4"        "nummail-4"            "sum.added.total-4"   
[29] "sum.removed.total-4"  "sum.added.file-4"     "CD-4"                 "max.file.changed-5"   "numjavafile-5"        "nummail-5"            "sum.added.total-5"   
[36] "sum.removed.total-5"  "sum.added.file-5"     "CD-5"                 "max.file.changed-6"   "numjavafile-6"        "nummail-6"            "sum.added.total-6"   
[43] "sum.removed.total-6"  "sum.added.file-6"     "sum.removed.file-6"   "CD-6"                 "max.file.changed-7"   "numjavafile-7"        "nummail-7"           
[50] "sum.added.total-7"    "sum.removed.total-7"  "sum.added.file-7"     "sum.removed.file-7"   "CD-7"                 "max.file.changed-8"   "numjavafile-8"       
[57] "nummail-8"            "sum.added.total-8"    "sum.removed.total-8"  "sum.added.file-8"     "sum.removed.file-8"   "CD-8"                 "max.file.changed-9"  
[64] "numjavafile-9"        "nummail-9"            "sum.added.total-9"    "sum.removed.total-9"  "sum.added.file-9"     "sum.removed.file-9"   "CD-9"                
[71] "max.file.changed-10"  "numjavafile-10"       "nummail-10"           "sum.added.total-10"   "sum.removed.total-10" "sum.added.file-10"    "sum.removed.file-10" 
[78] "CD-10"                "max.file.changed-11"  "numjavafile-11"       "nummail-11"           "sum.added.total-11"   "sum.removed.total-11" "sum.added.file-11"   
[85] "sum.removed.file-11"  "CD-11"                "max.file.changed-12"  "numjavafile-12"       "nummail-12"           "sum.added.total-12"   "sum.removed.total-12"
[92] "sum.added.file-12"    "sum.removed.file-12"  "CD-12"               
Aggregating results
Selecting tuning parameters
Fitting fL = 0, usekernel = FALSE, adjust = 1 on full training set
[1] "Model: nb"
 [1] "HL"                   "max.file.changed-1"   "numjavafile-1"        "nummail-1"            "sum.added.total-1"    "sum.removed.total-1"  "sum.added.file-1"    
 [8] "sum.removed.file-1"   "CD-1"                 "max.file.changed-2"   "numjavafile-2"        "nummail-2"            "sum.added.total-2"    "sum.removed.total-2" 
[15] "sum.added.file-2"     "CD-2"                 "max.file.changed-3"   "numjavafile-3"        "nummail-3"            "sum.added.total-3"    "sum.removed.total-3" 
[22] "sum.added.file-3"     "sum.removed.file-3"   "CD-3"                 "max.file.changed-4"   "numjavafile-4"        "nummail-4"            "sum.added.total-4"   
[29] "sum.removed.total-4"  "sum.added.file-4"     "CD-4"                 "max.file.changed-5"   "numjavafile-5"        "nummail-5"            "sum.added.total-5"   
[36] "sum.removed.total-5"  "sum.added.file-5"     "CD-5"                 "max.file.changed-6"   "numjavafile-6"        "nummail-6"            "sum.added.total-6"   
[43] "sum.removed.total-6"  "sum.added.file-6"     "sum.removed.file-6"   "CD-6"                 "max.file.changed-7"   "numjavafile-7"        "nummail-7"           
[50] "sum.added.total-7"    "sum.removed.total-7"  "sum.added.file-7"     "sum.removed.file-7"   "CD-7"                 "max.file.changed-8"   "numjavafile-8"       
[57] "nummail-8"            "sum.added.total-8"    "sum.removed.total-8"  "sum.added.file-8"     "sum.removed.file-8"   "CD-8"                 "max.file.changed-9"  
[64] "numjavafile-9"        "nummail-9"            "sum.added.total-9"    "sum.removed.total-9"  "sum.added.file-9"     "sum.removed.file-9"   "CD-9"                
[71] "max.file.changed-10"  "numjavafile-10"       "nummail-10"           "sum.added.total-10"   "sum.removed.total-10" "sum.added.file-10"    "sum.removed.file-10" 
[78] "CD-10"                "max.file.changed-11"  "numjavafile-11"       "nummail-11"           "sum.added.total-11"   "sum.removed.total-11" "sum.added.file-11"   
[85] "sum.removed.file-11"  "CD-11"                "max.file.changed-12"  "numjavafile-12"       "nummail-12"           "sum.added.total-12"   "sum.removed.total-12"
[92] "sum.added.file-12"    "sum.removed.file-12"  "CD-12"               
Aggregating results
Selecting tuning parameters
Fitting fL = 0, usekernel = FALSE, adjust = 1 on full training set
[1] "Model: nb"
 [1] "IXPD"                 "max.file.changed-1"   "numjavafile-1"        "nummail-1"            "sum.added.total-1"    "sum.removed.total-1"  "sum.added.file-1"    
 [8] "sum.removed.file-1"   "CD-1"                 "max.file.changed-2"   "numjavafile-2"        "nummail-2"            "sum.added.total-2"    "sum.removed.total-2" 
[15] "sum.added.file-2"     "CD-2"                 "max.file.changed-3"   "numjavafile-3"        "nummail-3"            "sum.added.total-3"    "sum.removed.total-3" 
[22] "sum.added.file-3"     "sum.removed.file-3"   "CD-3"                 "max.file.changed-4"   "numjavafile-4"        "nummail-4"            "sum.added.total-4"   
[29] "sum.removed.total-4"  "sum.added.file-4"     "CD-4"                 "max.file.changed-5"   "numjavafile-5"        "nummail-5"            "sum.added.total-5"   
[36] "sum.removed.total-5"  "sum.added.file-5"     "CD-5"                 "max.file.changed-6"   "numjavafile-6"        "nummail-6"            "sum.added.total-6"   
[43] "sum.removed.total-6"  "sum.added.file-6"     "sum.removed.file-6"   "CD-6"                 "max.file.changed-7"   "numjavafile-7"        "nummail-7"           
[50] "sum.added.total-7"    "sum.removed.total-7"  "sum.added.file-7"     "sum.removed.file-7"   "CD-7"                 "max.file.changed-8"   "numjavafile-8"       
[57] "nummail-8"            "sum.added.total-8"    "sum.removed.total-8"  "sum.added.file-8"     "sum.removed.file-8"   "CD-8"                 "max.file.changed-9"  
[64] "numjavafile-9"        "nummail-9"            "sum.added.total-9"    "sum.removed.total-9"  "sum.added.file-9"     "sum.removed.file-9"   "CD-9"                
[71] "max.file.changed-10"  "numjavafile-10"       "nummail-10"           "sum.added.total-10"   "sum.removed.total-10" "sum.added.file-10"    "sum.removed.file-10" 
[78] "CD-10"                "max.file.changed-11"  "numjavafile-11"       "nummail-11"           "sum.added.total-11"   "sum.removed.total-11" "sum.added.file-11"   
[85] "sum.removed.file-11"  "CD-11"                "max.file.changed-12"  "numjavafile-12"       "nummail-12"           "sum.added.total-12"   "sum.removed.total-12"
[92] "sum.added.file-12"    "sum.removed.file-12"  "CD-12"               
Aggregating results
Selecting tuning parameters
Fitting fL = 0, usekernel = TRUE, adjust = 1 on full training set
[1] "Model: C5.0"
 [1] "star"                 "max.file.changed-1"   "numjavafile-1"        "nummail-1"            "sum.added.total-1"    "sum.removed.total-1"  "sum.added.file-1"    
 [8] "sum.removed.file-1"   "CD-1"                 "max.file.changed-2"   "numjavafile-2"        "nummail-2"            "sum.added.total-2"    "sum.removed.total-2" 
[15] "sum.added.file-2"     "CD-2"                 "max.file.changed-3"   "numjavafile-3"        "nummail-3"            "sum.added.total-3"    "sum.removed.total-3" 
[22] "sum.added.file-3"     "sum.removed.file-3"   "CD-3"                 "max.file.changed-4"   "numjavafile-4"        "nummail-4"            "sum.added.total-4"   
[29] "sum.removed.total-4"  "sum.added.file-4"     "CD-4"                 "max.file.changed-5"   "numjavafile-5"        "nummail-5"            "sum.added.total-5"   
[36] "sum.removed.total-5"  "sum.added.file-5"     "CD-5"                 "max.file.changed-6"   "numjavafile-6"        "nummail-6"            "sum.added.total-6"   
[43] "sum.removed.total-6"  "sum.added.file-6"     "sum.removed.file-6"   "CD-6"                 "max.file.changed-7"   "numjavafile-7"        "nummail-7"           
[50] "sum.added.total-7"    "sum.removed.total-7"  "sum.added.file-7"     "sum.removed.file-7"   "CD-7"                 "max.file.changed-8"   "numjavafile-8"       
[57] "nummail-8"            "sum.added.total-8"    "sum.removed.total-8"  "sum.added.file-8"     "sum.removed.file-8"   "CD-8"                 "max.file.changed-9"  
[64] "numjavafile-9"        "nummail-9"            "sum.added.total-9"    "sum.removed.total-9"  "sum.added.file-9"     "sum.removed.file-9"   "CD-9"                
[71] "max.file.changed-10"  "numjavafile-10"       "nummail-10"           "sum.added.total-10"   "sum.removed.total-10" "sum.added.file-10"    "sum.removed.file-10" 
[78] "CD-10"                "max.file.changed-11"  "numjavafile-11"       "nummail-11"           "sum.added.total-11"   "sum.removed.total-11" "sum.added.file-11"   
[85] "sum.removed.file-11"  "CD-11"                "max.file.changed-12"  "numjavafile-12"       "nummail-12"           "sum.added.total-12"   "sum.removed.total-12"
[92] "sum.added.file-12"    "sum.removed.file-12"  "CD-12"               
Aggregating results
Selecting tuning parameters
Fitting trials = 10, model = tree, winnow = TRUE on full training set
[1] "Model: C5.0"
 [1] "circle"               "max.file.changed-1"   "numjavafile-1"        "nummail-1"            "sum.added.total-1"    "sum.removed.total-1"  "sum.added.file-1"    
 [8] "sum.removed.file-1"   "CD-1"                 "max.file.changed-2"   "numjavafile-2"        "nummail-2"            "sum.added.total-2"    "sum.removed.total-2" 
[15] "sum.added.file-2"     "CD-2"                 "max.file.changed-3"   "numjavafile-3"        "nummail-3"            "sum.added.total-3"    "sum.removed.total-3" 
[22] "sum.added.file-3"     "sum.removed.file-3"   "CD-3"                 "max.file.changed-4"   "numjavafile-4"        "nummail-4"            "sum.added.total-4"   
[29] "sum.removed.total-4"  "sum.added.file-4"     "CD-4"                 "max.file.changed-5"   "numjavafile-5"        "nummail-5"            "sum.added.total-5"   
[36] "sum.removed.total-5"  "sum.added.file-5"     "CD-5"                 "max.file.changed-6"   "numjavafile-6"        "nummail-6"            "sum.added.total-6"   
[43] "sum.removed.total-6"  "sum.added.file-6"     "sum.removed.file-6"   "CD-6"                 "max.file.changed-7"   "numjavafile-7"        "nummail-7"           
[50] "sum.added.total-7"    "sum.removed.total-7"  "sum.added.file-7"     "sum.removed.file-7"   "CD-7"                 "max.file.changed-8"   "numjavafile-8"       
[57] "nummail-8"            "sum.added.total-8"    "sum.removed.total-8"  "sum.added.file-8"     "sum.removed.file-8"   "CD-8"                 "max.file.changed-9"  
[64] "numjavafile-9"        "nummail-9"            "sum.added.total-9"    "sum.removed.total-9"  "sum.added.file-9"     "sum.removed.file-9"   "CD-9"                
[71] "max.file.changed-10"  "numjavafile-10"       "nummail-10"           "sum.added.total-10"   "sum.removed.total-10" "sum.added.file-10"    "sum.removed.file-10" 
[78] "CD-10"                "max.file.changed-11"  "numjavafile-11"       "nummail-11"           "sum.added.total-11"   "sum.removed.total-11" "sum.added.file-11"   
[85] "sum.removed.file-11"  "CD-11"                "max.file.changed-12"  "numjavafile-12"       "nummail-12"           "sum.added.total-12"   "sum.removed.total-12"
[92] "sum.added.file-12"    "sum.removed.file-12"  "CD-12"               
Aggregating results
Selecting tuning parameters
Fitting trials = 20, model = tree, winnow = FALSE on full training set
[1] "Model: C5.0"
 [1] "clique"               "max.file.changed-1"   "numjavafile-1"        "nummail-1"            "sum.added.total-1"    "sum.removed.total-1"  "sum.added.file-1"    
 [8] "sum.removed.file-1"   "CD-1"                 "max.file.changed-2"   "numjavafile-2"        "nummail-2"            "sum.added.total-2"    "sum.removed.total-2" 
[15] "sum.added.file-2"     "CD-2"                 "max.file.changed-3"   "numjavafile-3"        "nummail-3"            "sum.added.total-3"    "sum.removed.total-3" 
[22] "sum.added.file-3"     "sum.removed.file-3"   "CD-3"                 "max.file.changed-4"   "numjavafile-4"        "nummail-4"            "sum.added.total-4"   
[29] "sum.removed.total-4"  "sum.added.file-4"     "CD-4"                 "max.file.changed-5"   "numjavafile-5"        "nummail-5"            "sum.added.total-5"   
[36] "sum.removed.total-5"  "sum.added.file-5"     "CD-5"                 "max.file.changed-6"   "numjavafile-6"        "nummail-6"            "sum.added.total-6"   
[43] "sum.removed.total-6"  "sum.added.file-6"     "sum.removed.file-6"   "CD-6"                 "max.file.changed-7"   "numjavafile-7"        "nummail-7"           
[50] "sum.added.total-7"    "sum.removed.total-7"  "sum.added.file-7"     "sum.removed.file-7"   "CD-7"                 "max.file.changed-8"   "numjavafile-8"       
[57] "nummail-8"            "sum.added.total-8"    "sum.removed.total-8"  "sum.added.file-8"     "sum.removed.file-8"   "CD-8"                 "max.file.changed-9"  
[64] "numjavafile-9"        "nummail-9"            "sum.added.total-9"    "sum.removed.total-9"  "sum.added.file-9"     "sum.removed.file-9"   "CD-9"                
[71] "max.file.changed-10"  "numjavafile-10"       "nummail-10"           "sum.added.total-10"   "sum.removed.total-10" "sum.added.file-10"    "sum.removed.file-10" 
[78] "CD-10"                "max.file.changed-11"  "numjavafile-11"       "nummail-11"           "sum.added.total-11"   "sum.removed.total-11" "sum.added.file-11"   
[85] "sum.removed.file-11"  "CD-11"                "max.file.changed-12"  "numjavafile-12"       "nummail-12"           "sum.added.total-12"   "sum.removed.total-12"
[92] "sum.added.file-12"    "sum.removed.file-12"  "CD-12"               
Aggregating results
Selecting tuning parameters
Fitting trials = 20, model = tree, winnow = TRUE on full training set
[1] "Model: C5.0"
 [1] "chain"                "max.file.changed-1"   "numjavafile-1"        "nummail-1"            "sum.added.total-1"    "sum.removed.total-1"  "sum.added.file-1"    
 [8] "sum.removed.file-1"   "CD-1"                 "max.file.changed-2"   "numjavafile-2"        "nummail-2"            "sum.added.total-2"    "sum.removed.total-2" 
[15] "sum.added.file-2"     "CD-2"                 "max.file.changed-3"   "numjavafile-3"        "nummail-3"            "sum.added.total-3"    "sum.removed.total-3" 
[22] "sum.added.file-3"     "sum.removed.file-3"   "CD-3"                 "max.file.changed-4"   "numjavafile-4"        "nummail-4"            "sum.added.total-4"   
[29] "sum.removed.total-4"  "sum.added.file-4"     "CD-4"                 "max.file.changed-5"   "numjavafile-5"        "nummail-5"            "sum.added.total-5"   
[36] "sum.removed.total-5"  "sum.added.file-5"     "CD-5"                 "max.file.changed-6"   "numjavafile-6"        "nummail-6"            "sum.added.total-6"   
[43] "sum.removed.total-6"  "sum.added.file-6"     "sum.removed.file-6"   "CD-6"                 "max.file.changed-7"   "numjavafile-7"        "nummail-7"           
[50] "sum.added.total-7"    "sum.removed.total-7"  "sum.added.file-7"     "sum.removed.file-7"   "CD-7"                 "max.file.changed-8"   "numjavafile-8"       
[57] "nummail-8"            "sum.added.total-8"    "sum.removed.total-8"  "sum.added.file-8"     "sum.removed.file-8"   "CD-8"                 "max.file.changed-9"  
[64] "numjavafile-9"        "nummail-9"            "sum.added.total-9"    "sum.removed.total-9"  "sum.added.file-9"     "sum.removed.file-9"   "CD-9"                
[71] "max.file.changed-10"  "numjavafile-10"       "nummail-10"           "sum.added.total-10"   "sum.removed.total-10" "sum.added.file-10"    "sum.removed.file-10" 
[78] "CD-10"                "max.file.changed-11"  "numjavafile-11"       "nummail-11"           "sum.added.total-11"   "sum.removed.total-11" "sum.added.file-11"   
[85] "sum.removed.file-11"  "CD-11"                "max.file.changed-12"  "numjavafile-12"       "nummail-12"           "sum.added.total-12"   "sum.removed.total-12"
[92] "sum.added.file-12"    "sum.removed.file-12"  "CD-12"               
Aggregating results
Selecting tuning parameters
Fitting trials = 20, model = tree, winnow = FALSE on full training set
[1] "Model: C5.0"
 [1] "CD"                   "max.file.changed-1"   "numjavafile-1"        "nummail-1"            "sum.added.total-1"    "sum.removed.total-1"  "sum.added.file-1"    
 [8] "sum.removed.file-1"   "CD-1"                 "max.file.changed-2"   "numjavafile-2"        "nummail-2"            "sum.added.total-2"    "sum.removed.total-2" 
[15] "sum.added.file-2"     "CD-2"                 "max.file.changed-3"   "numjavafile-3"        "nummail-3"            "sum.added.total-3"    "sum.removed.total-3" 
[22] "sum.added.file-3"     "sum.removed.file-3"   "CD-3"                 "max.file.changed-4"   "numjavafile-4"        "nummail-4"            "sum.added.total-4"   
[29] "sum.removed.total-4"  "sum.added.file-4"     "CD-4"                 "max.file.changed-5"   "numjavafile-5"        "nummail-5"            "sum.added.total-5"   
[36] "sum.removed.total-5"  "sum.added.file-5"     "CD-5"                 "max.file.changed-6"   "numjavafile-6"        "nummail-6"            "sum.added.total-6"   
[43] "sum.removed.total-6"  "sum.added.file-6"     "sum.removed.file-6"   "CD-6"                 "max.file.changed-7"   "numjavafile-7"        "nummail-7"           
[50] "sum.added.total-7"    "sum.removed.total-7"  "sum.added.file-7"     "sum.removed.file-7"   "CD-7"                 "max.file.changed-8"   "numjavafile-8"       
[57] "nummail-8"            "sum.added.total-8"    "sum.removed.total-8"  "sum.added.file-8"     "sum.removed.file-8"   "CD-8"                 "max.file.changed-9"  
[64] "numjavafile-9"        "nummail-9"            "sum.added.total-9"    "sum.removed.total-9"  "sum.added.file-9"     "sum.removed.file-9"   "CD-9"                
[71] "max.file.changed-10"  "numjavafile-10"       "nummail-10"           "sum.added.total-10"   "sum.removed.total-10" "sum.added.file-10"    "sum.removed.file-10" 
[78] "CD-10"                "max.file.changed-11"  "numjavafile-11"       "nummail-11"           "sum.added.total-11"   "sum.removed.total-11" "sum.added.file-11"   
[85] "sum.removed.file-11"  "CD-11"                "max.file.changed-12"  "numjavafile-12"       "nummail-12"           "sum.added.total-12"   "sum.removed.total-12"
[92] "sum.added.file-12"    "sum.removed.file-12"  "CD-12"               
Aggregating results
Selecting tuning parameters
Fitting trials = 20, model = tree, winnow = FALSE on full training set
[1] "Model: C5.0"
 [1] "UD"                   "max.file.changed-1"   "numjavafile-1"        "nummail-1"            "sum.added.total-1"    "sum.removed.total-1"  "sum.added.file-1"    
 [8] "sum.removed.file-1"   "CD-1"                 "max.file.changed-2"   "numjavafile-2"        "nummail-2"            "sum.added.total-2"    "sum.removed.total-2" 
[15] "sum.added.file-2"     "CD-2"                 "max.file.changed-3"   "numjavafile-3"        "nummail-3"            "sum.added.total-3"    "sum.removed.total-3" 
[22] "sum.added.file-3"     "sum.removed.file-3"   "CD-3"                 "max.file.changed-4"   "numjavafile-4"        "nummail-4"            "sum.added.total-4"   
[29] "sum.removed.total-4"  "sum.added.file-4"     "CD-4"                 "max.file.changed-5"   "numjavafile-5"        "nummail-5"            "sum.added.total-5"   
[36] "sum.removed.total-5"  "sum.added.file-5"     "CD-5"                 "max.file.changed-6"   "numjavafile-6"        "nummail-6"            "sum.added.total-6"   
[43] "sum.removed.total-6"  "sum.added.file-6"     "sum.removed.file-6"   "CD-6"                 "max.file.changed-7"   "numjavafile-7"        "nummail-7"           
[50] "sum.added.total-7"    "sum.removed.total-7"  "sum.added.file-7"     "sum.removed.file-7"   "CD-7"                 "max.file.changed-8"   "numjavafile-8"       
[57] "nummail-8"            "sum.added.total-8"    "sum.removed.total-8"  "sum.added.file-8"     "sum.removed.file-8"   "CD-8"                 "max.file.changed-9"  
[64] "numjavafile-9"        "nummail-9"            "sum.added.total-9"    "sum.removed.total-9"  "sum.added.file-9"     "sum.removed.file-9"   "CD-9"                
[71] "max.file.changed-10"  "numjavafile-10"       "nummail-10"           "sum.added.total-10"   "sum.removed.total-10" "sum.added.file-10"    "sum.removed.file-10" 
[78] "CD-10"                "max.file.changed-11"  "numjavafile-11"       "nummail-11"           "sum.added.total-11"   "sum.removed.total-11" "sum.added.file-11"   
[85] "sum.removed.file-11"  "CD-11"                "max.file.changed-12"  "numjavafile-12"       "nummail-12"           "sum.added.total-12"   "sum.removed.total-12"
[92] "sum.added.file-12"    "sum.removed.file-12"  "CD-12"               
Aggregating results
Selecting tuning parameters
Fitting trials = 20, model = rules, winnow = FALSE on full training set
[1] "Model: C5.0"
 [1] "HL"                   "max.file.changed-1"   "numjavafile-1"        "nummail-1"            "sum.added.total-1"    "sum.removed.total-1"  "sum.added.file-1"    
 [8] "sum.removed.file-1"   "CD-1"                 "max.file.changed-2"   "numjavafile-2"        "nummail-2"            "sum.added.total-2"    "sum.removed.total-2" 
[15] "sum.added.file-2"     "CD-2"                 "max.file.changed-3"   "numjavafile-3"        "nummail-3"            "sum.added.total-3"    "sum.removed.total-3" 
[22] "sum.added.file-3"     "sum.removed.file-3"   "CD-3"                 "max.file.changed-4"   "numjavafile-4"        "nummail-4"            "sum.added.total-4"   
[29] "sum.removed.total-4"  "sum.added.file-4"     "CD-4"                 "max.file.changed-5"   "numjavafile-5"        "nummail-5"            "sum.added.total-5"   
[36] "sum.removed.total-5"  "sum.added.file-5"     "CD-5"                 "max.file.changed-6"   "numjavafile-6"        "nummail-6"            "sum.added.total-6"   
[43] "sum.removed.total-6"  "sum.added.file-6"     "sum.removed.file-6"   "CD-6"                 "max.file.changed-7"   "numjavafile-7"        "nummail-7"           
[50] "sum.added.total-7"    "sum.removed.total-7"  "sum.added.file-7"     "sum.removed.file-7"   "CD-7"                 "max.file.changed-8"   "numjavafile-8"       
[57] "nummail-8"            "sum.added.total-8"    "sum.removed.total-8"  "sum.added.file-8"     "sum.removed.file-8"   "CD-8"                 "max.file.changed-9"  
[64] "numjavafile-9"        "nummail-9"            "sum.added.total-9"    "sum.removed.total-9"  "sum.added.file-9"     "sum.removed.file-9"   "CD-9"                
[71] "max.file.changed-10"  "numjavafile-10"       "nummail-10"           "sum.added.total-10"   "sum.removed.total-10" "sum.added.file-10"    "sum.removed.file-10" 
[78] "CD-10"                "max.file.changed-11"  "numjavafile-11"       "nummail-11"           "sum.added.total-11"   "sum.removed.total-11" "sum.added.file-11"   
[85] "sum.removed.file-11"  "CD-11"                "max.file.changed-12"  "numjavafile-12"       "nummail-12"           "sum.added.total-12"   "sum.removed.total-12"
[92] "sum.added.file-12"    "sum.removed.file-12"  "CD-12"               
Aggregating results
Selecting tuning parameters
Fitting trials = 1, model = rules, winnow = FALSE on full training set
[1] "Model: C5.0"
 [1] "IXPD"                 "max.file.changed-1"   "numjavafile-1"        "nummail-1"            "sum.added.total-1"    "sum.removed.total-1"  "sum.added.file-1"    
 [8] "sum.removed.file-1"   "CD-1"                 "max.file.changed-2"   "numjavafile-2"        "nummail-2"            "sum.added.total-2"    "sum.removed.total-2" 
[15] "sum.added.file-2"     "CD-2"                 "max.file.changed-3"   "numjavafile-3"        "nummail-3"            "sum.added.total-3"    "sum.removed.total-3" 
[22] "sum.added.file-3"     "sum.removed.file-3"   "CD-3"                 "max.file.changed-4"   "numjavafile-4"        "nummail-4"            "sum.added.total-4"   
[29] "sum.removed.total-4"  "sum.added.file-4"     "CD-4"                 "max.file.changed-5"   "numjavafile-5"        "nummail-5"            "sum.added.total-5"   
[36] "sum.removed.total-5"  "sum.added.file-5"     "CD-5"                 "max.file.changed-6"   "numjavafile-6"        "nummail-6"            "sum.added.total-6"   
[43] "sum.removed.total-6"  "sum.added.file-6"     "sum.removed.file-6"   "CD-6"                 "max.file.changed-7"   "numjavafile-7"        "nummail-7"           
[50] "sum.added.total-7"    "sum.removed.total-7"  "sum.added.file-7"     "sum.removed.file-7"   "CD-7"                 "max.file.changed-8"   "numjavafile-8"       
[57] "nummail-8"            "sum.added.total-8"    "sum.removed.total-8"  "sum.added.file-8"     "sum.removed.file-8"   "CD-8"                 "max.file.changed-9"  
[64] "numjavafile-9"        "nummail-9"            "sum.added.total-9"    "sum.removed.total-9"  "sum.added.file-9"     "sum.removed.file-9"   "CD-9"                
[71] "max.file.changed-10"  "numjavafile-10"       "nummail-10"           "sum.added.total-10"   "sum.removed.total-10" "sum.added.file-10"    "sum.removed.file-10" 
[78] "CD-10"                "max.file.changed-11"  "numjavafile-11"       "nummail-11"           "sum.added.total-11"   "sum.removed.total-11" "sum.added.file-11"   
[85] "sum.removed.file-11"  "CD-11"                "max.file.changed-12"  "numjavafile-12"       "nummail-12"           "sum.added.total-12"   "sum.removed.total-12"
[92] "sum.added.file-12"    "sum.removed.file-12"  "CD-12"               
Aggregating results
Selecting tuning parameters
Fitting trials = 20, model = rules, winnow = FALSE on full training set
[1] "Model: rf"
 [1] "star"                 "max.file.changed-1"   "numjavafile-1"        "nummail-1"            "sum.added.total-1"    "sum.removed.total-1"  "sum.added.file-1"    
 [8] "sum.removed.file-1"   "CD-1"                 "max.file.changed-2"   "numjavafile-2"        "nummail-2"            "sum.added.total-2"    "sum.removed.total-2" 
[15] "sum.added.file-2"     "CD-2"                 "max.file.changed-3"   "numjavafile-3"        "nummail-3"            "sum.added.total-3"    "sum.removed.total-3" 
[22] "sum.added.file-3"     "sum.removed.file-3"   "CD-3"                 "max.file.changed-4"   "numjavafile-4"        "nummail-4"            "sum.added.total-4"   
[29] "sum.removed.total-4"  "sum.added.file-4"     "CD-4"                 "max.file.changed-5"   "numjavafile-5"        "nummail-5"            "sum.added.total-5"   
[36] "sum.removed.total-5"  "sum.added.file-5"     "CD-5"                 "max.file.changed-6"   "numjavafile-6"        "nummail-6"            "sum.added.total-6"   
[43] "sum.removed.total-6"  "sum.added.file-6"     "sum.removed.file-6"   "CD-6"                 "max.file.changed-7"   "numjavafile-7"        "nummail-7"           
[50] "sum.added.total-7"    "sum.removed.total-7"  "sum.added.file-7"     "sum.removed.file-7"   "CD-7"                 "max.file.changed-8"   "numjavafile-8"       
[57] "nummail-8"            "sum.added.total-8"    "sum.removed.total-8"  "sum.added.file-8"     "sum.removed.file-8"   "CD-8"                 "max.file.changed-9"  
[64] "numjavafile-9"        "nummail-9"            "sum.added.total-9"    "sum.removed.total-9"  "sum.added.file-9"     "sum.removed.file-9"   "CD-9"                
[71] "max.file.changed-10"  "numjavafile-10"       "nummail-10"           "sum.added.total-10"   "sum.removed.total-10" "sum.added.file-10"    "sum.removed.file-10" 
[78] "CD-10"                "max.file.changed-11"  "numjavafile-11"       "nummail-11"           "sum.added.total-11"   "sum.removed.total-11" "sum.added.file-11"   
[85] "sum.removed.file-11"  "CD-11"                "max.file.changed-12"  "numjavafile-12"       "nummail-12"           "sum.added.total-12"   "sum.removed.total-12"
[92] "sum.added.file-12"    "sum.removed.file-12"  "CD-12"               
Aggregating results
Selecting tuning parameters
Fitting mtry = 47 on full training set
[1] "Model: rf"
 [1] "circle"               "max.file.changed-1"   "numjavafile-1"        "nummail-1"            "sum.added.total-1"    "sum.removed.total-1"  "sum.added.file-1"    
 [8] "sum.removed.file-1"   "CD-1"                 "max.file.changed-2"   "numjavafile-2"        "nummail-2"            "sum.added.total-2"    "sum.removed.total-2" 
[15] "sum.added.file-2"     "CD-2"                 "max.file.changed-3"   "numjavafile-3"        "nummail-3"            "sum.added.total-3"    "sum.removed.total-3" 
[22] "sum.added.file-3"     "sum.removed.file-3"   "CD-3"                 "max.file.changed-4"   "numjavafile-4"        "nummail-4"            "sum.added.total-4"   
[29] "sum.removed.total-4"  "sum.added.file-4"     "CD-4"                 "max.file.changed-5"   "numjavafile-5"        "nummail-5"            "sum.added.total-5"   
[36] "sum.removed.total-5"  "sum.added.file-5"     "CD-5"                 "max.file.changed-6"   "numjavafile-6"        "nummail-6"            "sum.added.total-6"   
[43] "sum.removed.total-6"  "sum.added.file-6"     "sum.removed.file-6"   "CD-6"                 "max.file.changed-7"   "numjavafile-7"        "nummail-7"           
[50] "sum.added.total-7"    "sum.removed.total-7"  "sum.added.file-7"     "sum.removed.file-7"   "CD-7"                 "max.file.changed-8"   "numjavafile-8"       
[57] "nummail-8"            "sum.added.total-8"    "sum.removed.total-8"  "sum.added.file-8"     "sum.removed.file-8"   "CD-8"                 "max.file.changed-9"  
[64] "numjavafile-9"        "nummail-9"            "sum.added.total-9"    "sum.removed.total-9"  "sum.added.file-9"     "sum.removed.file-9"   "CD-9"                
[71] "max.file.changed-10"  "numjavafile-10"       "nummail-10"           "sum.added.total-10"   "sum.removed.total-10" "sum.added.file-10"    "sum.removed.file-10" 
[78] "CD-10"                "max.file.changed-11"  "numjavafile-11"       "nummail-11"           "sum.added.total-11"   "sum.removed.total-11" "sum.added.file-11"   
[85] "sum.removed.file-11"  "CD-11"                "max.file.changed-12"  "numjavafile-12"       "nummail-12"           "sum.added.total-12"   "sum.removed.total-12"
[92] "sum.added.file-12"    "sum.removed.file-12"  "CD-12"               
Aggregating results
Selecting tuning parameters
Fitting mtry = 93 on full training set
[1] "Model: rf"
 [1] "clique"               "max.file.changed-1"   "numjavafile-1"        "nummail-1"            "sum.added.total-1"    "sum.removed.total-1"  "sum.added.file-1"    
 [8] "sum.removed.file-1"   "CD-1"                 "max.file.changed-2"   "numjavafile-2"        "nummail-2"            "sum.added.total-2"    "sum.removed.total-2" 
[15] "sum.added.file-2"     "CD-2"                 "max.file.changed-3"   "numjavafile-3"        "nummail-3"            "sum.added.total-3"    "sum.removed.total-3" 
[22] "sum.added.file-3"     "sum.removed.file-3"   "CD-3"                 "max.file.changed-4"   "numjavafile-4"        "nummail-4"            "sum.added.total-4"   
[29] "sum.removed.total-4"  "sum.added.file-4"     "CD-4"                 "max.file.changed-5"   "numjavafile-5"        "nummail-5"            "sum.added.total-5"   
[36] "sum.removed.total-5"  "sum.added.file-5"     "CD-5"                 "max.file.changed-6"   "numjavafile-6"        "nummail-6"            "sum.added.total-6"   
[43] "sum.removed.total-6"  "sum.added.file-6"     "sum.removed.file-6"   "CD-6"                 "max.file.changed-7"   "numjavafile-7"        "nummail-7"           
[50] "sum.added.total-7"    "sum.removed.total-7"  "sum.added.file-7"     "sum.removed.file-7"   "CD-7"                 "max.file.changed-8"   "numjavafile-8"       
[57] "nummail-8"            "sum.added.total-8"    "sum.removed.total-8"  "sum.added.file-8"     "sum.removed.file-8"   "CD-8"                 "max.file.changed-9"  
[64] "numjavafile-9"        "nummail-9"            "sum.added.total-9"    "sum.removed.total-9"  "sum.added.file-9"     "sum.removed.file-9"   "CD-9"                
[71] "max.file.changed-10"  "numjavafile-10"       "nummail-10"           "sum.added.total-10"   "sum.removed.total-10" "sum.added.file-10"    "sum.removed.file-10" 
[78] "CD-10"                "max.file.changed-11"  "numjavafile-11"       "nummail-11"           "sum.added.total-11"   "sum.removed.total-11" "sum.added.file-11"   
[85] "sum.removed.file-11"  "CD-11"                "max.file.changed-12"  "numjavafile-12"       "nummail-12"           "sum.added.total-12"   "sum.removed.total-12"
[92] "sum.added.file-12"    "sum.removed.file-12"  "CD-12"               
Aggregating results
Selecting tuning parameters
Fitting mtry = 47 on full training set
[1] "Model: rf"
 [1] "chain"                "max.file.changed-1"   "numjavafile-1"        "nummail-1"            "sum.added.total-1"    "sum.removed.total-1"  "sum.added.file-1"    
 [8] "sum.removed.file-1"   "CD-1"                 "max.file.changed-2"   "numjavafile-2"        "nummail-2"            "sum.added.total-2"    "sum.removed.total-2" 
[15] "sum.added.file-2"     "CD-2"                 "max.file.changed-3"   "numjavafile-3"        "nummail-3"            "sum.added.total-3"    "sum.removed.total-3" 
[22] "sum.added.file-3"     "sum.removed.file-3"   "CD-3"                 "max.file.changed-4"   "numjavafile-4"        "nummail-4"            "sum.added.total-4"   
[29] "sum.removed.total-4"  "sum.added.file-4"     "CD-4"                 "max.file.changed-5"   "numjavafile-5"        "nummail-5"            "sum.added.total-5"   
[36] "sum.removed.total-5"  "sum.added.file-5"     "CD-5"                 "max.file.changed-6"   "numjavafile-6"        "nummail-6"            "sum.added.total-6"   
[43] "sum.removed.total-6"  "sum.added.file-6"     "sum.removed.file-6"   "CD-6"                 "max.file.changed-7"   "numjavafile-7"        "nummail-7"           
[50] "sum.added.total-7"    "sum.removed.total-7"  "sum.added.file-7"     "sum.removed.file-7"   "CD-7"                 "max.file.changed-8"   "numjavafile-8"       
[57] "nummail-8"            "sum.added.total-8"    "sum.removed.total-8"  "sum.added.file-8"     "sum.removed.file-8"   "CD-8"                 "max.file.changed-9"  
[64] "numjavafile-9"        "nummail-9"            "sum.added.total-9"    "sum.removed.total-9"  "sum.added.file-9"     "sum.removed.file-9"   "CD-9"                
[71] "max.file.changed-10"  "numjavafile-10"       "nummail-10"           "sum.added.total-10"   "sum.removed.total-10" "sum.added.file-10"    "sum.removed.file-10" 
[78] "CD-10"                "max.file.changed-11"  "numjavafile-11"       "nummail-11"           "sum.added.total-11"   "sum.removed.total-11" "sum.added.file-11"   
[85] "sum.removed.file-11"  "CD-11"                "max.file.changed-12"  "numjavafile-12"       "nummail-12"           "sum.added.total-12"   "sum.removed.total-12"
[92] "sum.added.file-12"    "sum.removed.file-12"  "CD-12"               
Aggregating results
Selecting tuning parameters
Fitting mtry = 47 on full training set
[1] "Model: rf"
 [1] "CD"                   "max.file.changed-1"   "numjavafile-1"        "nummail-1"            "sum.added.total-1"    "sum.removed.total-1"  "sum.added.file-1"    
 [8] "sum.removed.file-1"   "CD-1"                 "max.file.changed-2"   "numjavafile-2"        "nummail-2"            "sum.added.total-2"    "sum.removed.total-2" 
[15] "sum.added.file-2"     "CD-2"                 "max.file.changed-3"   "numjavafile-3"        "nummail-3"            "sum.added.total-3"    "sum.removed.total-3" 
[22] "sum.added.file-3"     "sum.removed.file-3"   "CD-3"                 "max.file.changed-4"   "numjavafile-4"        "nummail-4"            "sum.added.total-4"   
[29] "sum.removed.total-4"  "sum.added.file-4"     "CD-4"                 "max.file.changed-5"   "numjavafile-5"        "nummail-5"            "sum.added.total-5"   
[36] "sum.removed.total-5"  "sum.added.file-5"     "CD-5"                 "max.file.changed-6"   "numjavafile-6"        "nummail-6"            "sum.added.total-6"   
[43] "sum.removed.total-6"  "sum.added.file-6"     "sum.removed.file-6"   "CD-6"                 "max.file.changed-7"   "numjavafile-7"        "nummail-7"           
[50] "sum.added.total-7"    "sum.removed.total-7"  "sum.added.file-7"     "sum.removed.file-7"   "CD-7"                 "max.file.changed-8"   "numjavafile-8"       
[57] "nummail-8"            "sum.added.total-8"    "sum.removed.total-8"  "sum.added.file-8"     "sum.removed.file-8"   "CD-8"                 "max.file.changed-9"  
[64] "numjavafile-9"        "nummail-9"            "sum.added.total-9"    "sum.removed.total-9"  "sum.added.file-9"     "sum.removed.file-9"   "CD-9"                
[71] "max.file.changed-10"  "numjavafile-10"       "nummail-10"           "sum.added.total-10"   "sum.removed.total-10" "sum.added.file-10"    "sum.removed.file-10" 
[78] "CD-10"                "max.file.changed-11"  "numjavafile-11"       "nummail-11"           "sum.added.total-11"   "sum.removed.total-11" "sum.added.file-11"   
[85] "sum.removed.file-11"  "CD-11"                "max.file.changed-12"  "numjavafile-12"       "nummail-12"           "sum.added.total-12"   "sum.removed.total-12"
[92] "sum.added.file-12"    "sum.removed.file-12"  "CD-12"               
Aggregating results
Selecting tuning parameters
Fitting mtry = 47 on full training set
[1] "Model: rf"
 [1] "UD"                   "max.file.changed-1"   "numjavafile-1"        "nummail-1"            "sum.added.total-1"    "sum.removed.total-1"  "sum.added.file-1"    
 [8] "sum.removed.file-1"   "CD-1"                 "max.file.changed-2"   "numjavafile-2"        "nummail-2"            "sum.added.total-2"    "sum.removed.total-2" 
[15] "sum.added.file-2"     "CD-2"                 "max.file.changed-3"   "numjavafile-3"        "nummail-3"            "sum.added.total-3"    "sum.removed.total-3" 
[22] "sum.added.file-3"     "sum.removed.file-3"   "CD-3"                 "max.file.changed-4"   "numjavafile-4"        "nummail-4"            "sum.added.total-4"   
[29] "sum.removed.total-4"  "sum.added.file-4"     "CD-4"                 "max.file.changed-5"   "numjavafile-5"        "nummail-5"            "sum.added.total-5"   
[36] "sum.removed.total-5"  "sum.added.file-5"     "CD-5"                 "max.file.changed-6"   "numjavafile-6"        "nummail-6"            "sum.added.total-6"   
[43] "sum.removed.total-6"  "sum.added.file-6"     "sum.removed.file-6"   "CD-6"                 "max.file.changed-7"   "numjavafile-7"        "nummail-7"           
[50] "sum.added.total-7"    "sum.removed.total-7"  "sum.added.file-7"     "sum.removed.file-7"   "CD-7"                 "max.file.changed-8"   "numjavafile-8"       
[57] "nummail-8"            "sum.added.total-8"    "sum.removed.total-8"  "sum.added.file-8"     "sum.removed.file-8"   "CD-8"                 "max.file.changed-9"  
[64] "numjavafile-9"        "nummail-9"            "sum.added.total-9"    "sum.removed.total-9"  "sum.added.file-9"     "sum.removed.file-9"   "CD-9"                
[71] "max.file.changed-10"  "numjavafile-10"       "nummail-10"           "sum.added.total-10"   "sum.removed.total-10" "sum.added.file-10"    "sum.removed.file-10" 
[78] "CD-10"                "max.file.changed-11"  "numjavafile-11"       "nummail-11"           "sum.added.total-11"   "sum.removed.total-11" "sum.added.file-11"   
[85] "sum.removed.file-11"  "CD-11"                "max.file.changed-12"  "numjavafile-12"       "nummail-12"           "sum.added.total-12"   "sum.removed.total-12"
[92] "sum.added.file-12"    "sum.removed.file-12"  "CD-12"               
Aggregating results
Selecting tuning parameters
Fitting mtry = 2 on full training set
[1] "Model: rf"
 [1] "HL"                   "max.file.changed-1"   "numjavafile-1"        "nummail-1"            "sum.added.total-1"    "sum.removed.total-1"  "sum.added.file-1"    
 [8] "sum.removed.file-1"   "CD-1"                 "max.file.changed-2"   "numjavafile-2"        "nummail-2"            "sum.added.total-2"    "sum.removed.total-2" 
[15] "sum.added.file-2"     "CD-2"                 "max.file.changed-3"   "numjavafile-3"        "nummail-3"            "sum.added.total-3"    "sum.removed.total-3" 
[22] "sum.added.file-3"     "sum.removed.file-3"   "CD-3"                 "max.file.changed-4"   "numjavafile-4"        "nummail-4"            "sum.added.total-4"   
[29] "sum.removed.total-4"  "sum.added.file-4"     "CD-4"                 "max.file.changed-5"   "numjavafile-5"        "nummail-5"            "sum.added.total-5"   
[36] "sum.removed.total-5"  "sum.added.file-5"     "CD-5"                 "max.file.changed-6"   "numjavafile-6"        "nummail-6"            "sum.added.total-6"   
[43] "sum.removed.total-6"  "sum.added.file-6"     "sum.removed.file-6"   "CD-6"                 "max.file.changed-7"   "numjavafile-7"        "nummail-7"           
[50] "sum.added.total-7"    "sum.removed.total-7"  "sum.added.file-7"     "sum.removed.file-7"   "CD-7"                 "max.file.changed-8"   "numjavafile-8"       
[57] "nummail-8"            "sum.added.total-8"    "sum.removed.total-8"  "sum.added.file-8"     "sum.removed.file-8"   "CD-8"                 "max.file.changed-9"  
[64] "numjavafile-9"        "nummail-9"            "sum.added.total-9"    "sum.removed.total-9"  "sum.added.file-9"     "sum.removed.file-9"   "CD-9"                
[71] "max.file.changed-10"  "numjavafile-10"       "nummail-10"           "sum.added.total-10"   "sum.removed.total-10" "sum.added.file-10"    "sum.removed.file-10" 
[78] "CD-10"                "max.file.changed-11"  "numjavafile-11"       "nummail-11"           "sum.added.total-11"   "sum.removed.total-11" "sum.added.file-11"   
[85] "sum.removed.file-11"  "CD-11"                "max.file.changed-12"  "numjavafile-12"       "nummail-12"           "sum.added.total-12"   "sum.removed.total-12"
[92] "sum.added.file-12"    "sum.removed.file-12"  "CD-12"               
Aggregating results
Selecting tuning parameters
Fitting mtry = 93 on full training set
[1] "Model: rf"
 [1] "IXPD"                 "max.file.changed-1"   "numjavafile-1"        "nummail-1"            "sum.added.total-1"    "sum.removed.total-1"  "sum.added.file-1"    
 [8] "sum.removed.file-1"   "CD-1"                 "max.file.changed-2"   "numjavafile-2"        "nummail-2"            "sum.added.total-2"    "sum.removed.total-2" 
[15] "sum.added.file-2"     "CD-2"                 "max.file.changed-3"   "numjavafile-3"        "nummail-3"            "sum.added.total-3"    "sum.removed.total-3" 
[22] "sum.added.file-3"     "sum.removed.file-3"   "CD-3"                 "max.file.changed-4"   "numjavafile-4"        "nummail-4"            "sum.added.total-4"   
[29] "sum.removed.total-4"  "sum.added.file-4"     "CD-4"                 "max.file.changed-5"   "numjavafile-5"        "nummail-5"            "sum.added.total-5"   
[36] "sum.removed.total-5"  "sum.added.file-5"     "CD-5"                 "max.file.changed-6"   "numjavafile-6"        "nummail-6"            "sum.added.total-6"   
[43] "sum.removed.total-6"  "sum.added.file-6"     "sum.removed.file-6"   "CD-6"                 "max.file.changed-7"   "numjavafile-7"        "nummail-7"           
[50] "sum.added.total-7"    "sum.removed.total-7"  "sum.added.file-7"     "sum.removed.file-7"   "CD-7"                 "max.file.changed-8"   "numjavafile-8"       
[57] "nummail-8"            "sum.added.total-8"    "sum.removed.total-8"  "sum.added.file-8"     "sum.removed.file-8"   "CD-8"                 "max.file.changed-9"  
[64] "numjavafile-9"        "nummail-9"            "sum.added.total-9"    "sum.removed.total-9"  "sum.added.file-9"     "sum.removed.file-9"   "CD-9"                
[71] "max.file.changed-10"  "numjavafile-10"       "nummail-10"           "sum.added.total-10"   "sum.removed.total-10" "sum.added.file-10"    "sum.removed.file-10" 
[78] "CD-10"                "max.file.changed-11"  "numjavafile-11"       "nummail-11"           "sum.added.total-11"   "sum.removed.total-11" "sum.added.file-11"   
[85] "sum.removed.file-11"  "CD-11"                "max.file.changed-12"  "numjavafile-12"       "nummail-12"           "sum.added.total-12"   "sum.removed.total-12"
[92] "sum.added.file-12"    "sum.removed.file-12"  "CD-12"               
Aggregating results
Selecting tuning parameters
Fitting mtry = 2 on full training set

```{r train nb and all targets}
models <- c("nb") # "C5.0" "logreg" has some issues, should be tested outside
set.seed(825)
confusionMatricesNB <- runCV(pkg.dataset.nzv, models, targets, "dev.jgit-month-")
write.csv(confusionMatricesNB, "dev.jgit-month-cm-ALL-nb.csv")
#```

#```{r train C5.0 and all targets}
models <- c("C5.0") # "C5.0" "logreg" has some issues, should be tested outside
set.seed(825)
confusionMatricesC50 <- runCV(pkg.dataset.nzv, models, targets, "dev.jgit-month-")
write.csv(confusionMatricesC50, "dev.jgit-month-cm-ALL-c50.csv")
#```


#```{r train rf and all targets}
models <- c("rf") # "C5.0" "logreg" has some issues, should be tested outside
set.seed(825)
confusionMatricesRF <- runCV(pkg.dataset.nzv, models, targets, "dev.jgit-month-")
write.csv(confusionMatricesRF, "dev.jgit-month-cm-ALL-rf.csv")
#```

#```{r write all confusion matrices}
write.csv(rbind(confusionMatricesNB, confusionMatricesC50, confusionMatricesRF), "dev.jgit-month-cm-ALL-ALL.csv")
```



```{r train nb and all targets}
models <- c("nb") # "C5.0" "logreg" has some issues, should be tested outside
set.seed(825)
confusionMatricesNB <- runCV.smote(pkg.dataset.nzv, models, targets, "smote.dev.jgit-month-")
write.csv(confusionMatricesNB, "smote.dev.jgit-month-cm-ALL-nb.csv")
#```

#```{r train C5.0 and all targets}
models <- c("C5.0") # "C5.0" "logreg" has some issues, should be tested outside
set.seed(825)
confusionMatricesC50 <- runCV.smote(pkg.dataset.nzv, models, targets, "smote.dev.jgit-month-")
write.csv(confusionMatricesC50, "smote.dev.jgit-month-cm-ALL-c50.csv")
#```


#```{r train rf and all targets}
models <- c("rf") # "C5.0" "logreg" has some issues, should be tested outside
set.seed(825)
confusionMatricesRF <- runCV.smote(pkg.dataset.nzv, models, targets, "smote.dev.jgit-month-")
write.csv(confusionMatricesRF, "smote.dev.jgit-month-cm-ALL-rf.csv")
#```

#```{r write all confusion matrices}
write.csv(rbind(confusionMatricesNB, confusionMatricesC50, confusionMatricesRF), "smote.dev.jgit-month-cm-ALL-ALL.csv")
```

```{r train svm and all targets}
shapes <- c("star", "circle", "tiny", "clique", "chain")
targets <- c(shapes, "CD", "UD", "HL", "IXPD")
pkg.dataset.svm <- subset(pkg.lagged, select = -c(commit_date, package))
head(pkg.dataset)
n <- names(pkg.dataset.svm)
#tfcutter <- colwise(cut, breaks = c(0, 1, .Machine$integer.max), labels = c(0, 1), right = FALSE, ordered_result = TRUE)
#pkg.dataset <- cbind(tfcutter(pkg.dataset[targets]), pkg.dataset[setdiff(names(pkg.dataset), targets)])
# Remove columns with near-zero variance

range01 <- function(x) {(x - min(x)) / (max(x) - min(x)) }
    pkg.dataset.svm.t <- apply(pkg.dataset.svm[setdiff(names(pkg.dataset.svm), targets)], 2, range01)
    pkg.dataset.svm <- cbind(ifelse(pkg.dataset.svm[targets]<1,0,1), pkg.dataset.svm.t)
    rm(pkg.dataset.svm.t)
    pkg.dataset.svm <- as.data.frame(pkg.dataset.svm)
	#names(pkg.dataset.svm) <- n
    head(pkg.dataset.svm)
    #pkg.dataset.svm <- as.data.frame(cbind(pkg.dataset.svm[c("star","tiny", "clique", "chain", "CD", "UD", "IXPD")], ifelse(pkg.dataset.svm[grep("-",names(pkg.dataset.svm))]<1,0,1)))
pkg.dataset.svm <- pkg.dataset.svm[, -nearZeroVar(pkg.dataset.svm)]
pkg.dataset.nzv <- pkg.dataset.svm

fitControl.svm <- trainControl(## 10-fold CV
            method = "repeatedcv"
            #,number = 10
						## repeated ten times
            ,repeats = 5
            ,verboseIter = TRUE
						#,classProbs=TRUE
						,savePredictions = TRUE
						#,sampling = "down"
            #,summaryFunction = twoClassSummary # Use AUC to pick the best model
						)


# define a function to encapsulate the training procedure
runCV.svm <- function(lagged, .grid, .models, .targets, .outfilePrefix = "") {
        # Generate all combinations of targets and models to test
    #experiments <- expand.grid(shape = .shapes, model = .models)
    #models <- c(  "svmLinear","svmRadial")
    experiments <- expand.grid(shape = .targets, model = .models)
	#lagged = pkg.dataset.nzv
    print(experiments)
    #head(lagged)
    #names(lagged)
    adply(experiments, .margins = 1, function(experiment) {
        currentShape <- paste(experiment[1, "shape"])
        currentModel <- paste(experiment[1, "model"])
        #print(paste("Model:", currentModel))
        #print(paste("Col lagged:", names(lagged)))
        if (currentShape %in% names(lagged)) {
            # Keep only lagged columns in the dataset, plus the class
            lagged.train <- cbind(lagged[c(currentShape)],
                            lagged[grep("-", names(lagged))])
            trainIndex <- createDataPartition(lagged.train[,currentShape], p=.5,list = FALSE)
            trainData <- lagged.train[trainIndex,]
            testData <- lagged.train[-trainIndex,]
            lagged.train<-trainData
            print(paste("Model:", currentModel))
            print(names(lagged.train))
            fit <- train(
			          #as.formula(paste(currentShape, " ~ .",sep = "")),
                # data = lagged.train,
                #y = paste("lagged.train$", currentShape, sep = ""),
                y = factor(model.matrix(~. - 1, lagged.train[currentShape])),
                x = model.matrix(~. - 1, lagged.train),
                method = currentModel,
                tuneGrid = .grid, 
                #tuneLength =9,# 9 values of the cost function
                preProc = c("center", "scale"), # Center and scale data
                trControl = fitControl.svm)
            print(fit)
            test_pred = predict(fit,newData=model.matrix(~. - 1,testData))
            print("predictiton test", test_pred)
            #cm <- confusionMatrix(test_pred,testData[,currentShape])
            cm<-confusionMatrix(fit$pred$pred, fit$pred$obs,positive = "1", mode = "prec_recall")
    				
            #cm <- confusionMatrix(confusionMatrix(fit, norm = "none")$table,
            #                   positive = "1",
            #                   mode = "prec_recall")
            
            cm.df <- data.frame(as.list(cm$overall), as.list(cm$byClass))
            write.csv(cm.df, paste0(.outfilePrefix, "cm-", currentShape, "-", currentModel, ".csv"))
			saveRDS(fit, paste0(.outfilePrefix, "model-", currentShape, "-", currentModel, ".rds"))
            cm.df
        } else {
            data.frame()
        }
    })
}
```

```{r}
models <- c("svmRadial") # "C5.0" "logreg" has some issues, should be tested outside
set.seed(825)
    grid <- expand.grid(sigma = c(.5, .6, .7, .8, .9, 1, 1.2, 1.4), C = c(1.25, 1.5, 1.75, 2, 2.25))
    grid <- expand.grid(sigma = c(.05, .07, .1, .15, .17, .2, .25, .3, .35, .4), C = c(.5, 1.0, 1.25, 1.5, 2,4,8,10))
confusionMatricesSVMRadial <- runCV.svm(pkg.dataset.nzv, grid, models, targets, "dev.jgit-month-")
write.csv(confusionMatricesSVMRadial, "dev.jgit-month-cm-ALL-svm-radial.csv")
#```

#```{r}
models <- c("svmLinear") # "C5.0" "logreg" has some issues, should be tested outside
set.seed(825)
#head(pkg.dataset.nzv)
#names(pkg.dataset.nzv)
grid <- expand.grid(C = c(0.01,0.05,0.1,0.5,0.75,0.9, 1, 1.1, 1.25, 2, 4, 8, 10))
confusionMatricesSVMlinear <- runCV.svm(pkg.dataset.nzv, grid, models, targets, "dev.jgit-month-")
write.csv(confusionMatricesSVMlinear, "dev.jgit-month-cm-ALL-svm-linear.csv")
```

[1] "Model: C5.0"
 [1] "star" 
 [2] "CD-1"  "CA-1"  "CE-1"  "RMI-1" "RMA-1" "RMD-1" "CD-2"  "CA-2"  "CE-2"  "RMI-2" "RMA-2" "RMD-2" "CD-3"  "CA-3"  "CE-3"  "RMI-3" "RMA-3" "RMD-3" "CD-4"  "CA-4"  "CE-4"  "RMI-4" "RMA-4" "RMD-4" "CD-5" "CA-5"  "CE-5"  "RMI-5" "RMA-5" "RMD-5"
Loading required package: C50
package C50 was built under R version 3.3.2Aggregating results
Selecting tuning parameters
Fitting trials = 20, model = tree, winnow = TRUE on full training set
[1] "Model: C5.0"
 [1] "circle" 
 [2] "CD-1"   "CA-1"   "CE-1"   "RMI-1"  "RMA-1"  "RMD-1"  "CD-2"   "CA-2"   "CE-2"   "RMI-2"  "RMA-2" "RMD-2"  "CD-3"   "CA-3"   "CE-3"   "RMI-3"  "RMA-3"  "RMD-3"  "CD-4"   "CA-4"   "CE-4"   "RMI-4"  "RMA-4" "RMD-4"  "CD-5"   "CA-5"   "CE-5"   "RMI-5"  "RMA-5"  "RMD-5" 
Aggregating results
Selecting tuning parameters
Fitting trials = 20, model = rules, winnow = TRUE on full training set
[1] "Model: C5.0"
 [1] "clique" 
 [2] "CD-1"   "CA-1"   "CE-1"   "RMI-1"  "RMA-1"  "RMD-1"  "CD-2"   "CA-2"   "CE-2"   "RMI-2"  "RMA-2" "RMD-2"  "CD-3"   "CA-3"   "CE-3"   "RMI-3"  "RMA-3"  "RMD-3"  "CD-4"   "CA-4"   "CE-4"   "RMI-4"  "RMA-4" "RMD-4"  "CD-5"   "CA-5"   "CE-5"   "RMI-5"  "RMA-5"  "RMD-5" 
Aggregating results
Selecting tuning parameters
Fitting trials = 20, model = rules, winnow = FALSE on full training set
[1] "Model: C5.0"
 [1] "chain"
 [2] "CD-1"  "CA-1"  "CE-1"  "RMI-1" "RMA-1" "RMD-1" "CD-2"  "CA-2"  "CE-2"  "RMI-2" "RMA-2" "RMD-2" "CD-3"  "CA-3"  "CE-3"  "RMI-3" "RMA-3" "RMD-3" "CD-4"  "CA-4"  "CE-4"  "RMI-4" "RMA-4" "RMD-4" "CD-5" "CA-5"  "CE-5"  "RMI-5" "RMA-5" "RMD-5"
Aggregating results
Selecting tuning parameters
Fitting trials = 20, model = tree, winnow = TRUE on full training set
[1] "Model: C5.0"
 [1] "CD"  
 [2] "CD-1"  "CA-1"  "CE-1"  "RMI-1" "RMA-1" "RMD-1" "CD-2"  "CA-2"  "CE-2"  "RMI-2" "RMA-2" "RMD-2" "CD-3"  "CA-3"  "CE-3"  "RMI-3" "RMA-3" "RMD-3" "CD-4"  "CA-4"  "CE-4"  "RMI-4" "RMA-4" "RMD-4" "CD-5" "CA-5"  "CE-5"  "RMI-5" "RMA-5" "RMD-5"
Aggregating results
Selecting tuning parameters
Fitting trials = 20, model = rules, winnow = FALSE on full training set
[1] "Model: C5.0"
 [1] "UD"  
 [2] "CD-1"  "CA-1"  "CE-1"  "RMI-1" "RMA-1" "RMD-1" "CD-2"  "CA-2"  "CE-2"  "RMI-2" "RMA-2" "RMD-2" "CD-3"  "CA-3"  "CE-3"  "RMI-3" "RMA-3" "RMD-3" "CD-4"  "CA-4"  "CE-4"  "RMI-4" "RMA-4" "RMD-4" "CD-5" "CA-5"  "CE-5"  "RMI-5" "RMA-5" "RMD-5"
Aggregating results
Selecting tuning parameters
Fitting trials = 20, model = rules, winnow = FALSE on full training set
[1] "Model: C5.0"
 [1] "HL"    
 [2] "CD-1"  "CA-1"  "CE-1"  "RMI-1" "RMA-1" "RMD-1" "CD-2"  "CA-2"  "CE-2"  "RMI-2" "RMA-2" "RMD-2" "CD-3"  "CA-3"  "CE-3"  "RMI-3" "RMA-3" "RMD-3" "CD-4"  "CA-4"  "CE-4"  "RMI-4" "RMA-4" "RMD-4" "CD-5" "CA-5"  "CE-5"  "RMI-5" "RMA-5" "RMD-5"
Aggregating results
Selecting tuning parameters
Fitting trials = 20, model = rules, winnow = FALSE on full training set
[1] "Model: C5.0"
 [1] "IXPD" 
 [2] "CD-1"  "CA-1"  "CE-1"  "RMI-1" "RMA-1" "RMD-1" "CD-2"  "CA-2"  "CE-2"  "RMI-2" "RMA-2" "RMD-2" "CD-3"  "CA-3"  "CE-3"  "RMI-3" "RMA-3" "RMD-3" "CD-4"  "CA-4"  "CE-4"  "RMI-4" "RMA-4" "RMD-4" "CD-5" "CA-5"  "CE-5"  "RMI-5" "RMA-5" "RMD-5"
Aggregating results
Selecting tuning parameters
Fitting trials = 20, model = rules, winnow = FALSE on full training set


#new
[1] "Model: C5.0"
 [1] "star"  "CD-1"  "CD-2"  "CD-3"  "CD-4"  "CD-5"  "CD-6"  "CD-7"  "CD-8"  "CD-9"  "CD-10" "CD-11" "CD-12"
Aggregating results
Selecting tuning parameters
Fitting trials = 1, model = tree, winnow = TRUE on full training set
[1] "Model: C5.0"
 [1] "circle" "CD-1"   "CD-2"   "CD-3"   "CD-4"   "CD-5"   "CD-6"   "CD-7"   "CD-8"   "CD-9"   "CD-10"  "CD-11"  "CD-12" 
Aggregating results
Selecting tuning parameters
Fitting trials = 20, model = tree, winnow = FALSE on full training set
[1] "Model: C5.0"
 [1] "clique" "CD-1"   "CD-2"   "CD-3"   "CD-4"   "CD-5"   "CD-6"   "CD-7"   "CD-8"   "CD-9"   "CD-10"  "CD-11"  "CD-12" 
Aggregating results
Selecting tuning parameters
Fitting trials = 20, model = tree, winnow = FALSE on full training set
[1] "Model: C5.0"
 [1] "chain" "CD-1"  "CD-2"  "CD-3"  "CD-4"  "CD-5"  "CD-6"  "CD-7"  "CD-8"  "CD-9"  "CD-10" "CD-11" "CD-12"
Aggregating results
Selecting tuning parameters
Fitting trials = 10, model = tree, winnow = FALSE on full training set
[1] "Model: C5.0"
 [1] "CD"    "CD-1"  "CD-2"  "CD-3"  "CD-4"  "CD-5"  "CD-6"  "CD-7"  "CD-8"  "CD-9"  "CD-10" "CD-11" "CD-12"
Aggregating results
Selecting tuning parameters
Fitting trials = 20, model = tree, winnow = FALSE on full training set
[1] "Model: C5.0"
 [1] "UD"    "CD-1"  "CD-2"  "CD-3"  "CD-4"  "CD-5"  "CD-6"  "CD-7"  "CD-8"  "CD-9"  "CD-10" "CD-11" "CD-12"
Aggregating results
Selecting tuning parameters
Fitting trials = 1, model = tree, winnow = FALSE on full training set
[1] "Model: C5.0"
 [1] "HL"    "CD-1"  "CD-2"  "CD-3"  "CD-4"  "CD-5"  "CD-6"  "CD-7"  "CD-8"  "CD-9"  "CD-10" "CD-11" "CD-12"
Aggregating results
Selecting tuning parameters
Fitting trials = 10, model = rules, winnow = FALSE on full training set
[1] "Model: C5.0"
 [1] "IXPD"  "CD-1"  "CD-2"  "CD-3"  "CD-4"  "CD-5"  "CD-6"  "CD-7"  "CD-8"  "CD-9"  "CD-10" "CD-11" "CD-12"
Aggregating results
Selecting tuning parameters
Fitting trials = 1, model = rules, winnow = TRUE on full training set

[1] "Model: rf"
 [1] "star"  "CD-1"  "CD-2"  "CD-3"  "CD-4"  "CD-5"  "CD-6"  "CD-7"  "CD-8"  "CD-9"  "CD-10" "CD-11" "CD-12"
Aggregating results
Selecting tuning parameters
Fitting mtry = 2 on full training set
[1] "Model: rf"
 [1] "circle" "CD-1"   "CD-2"   "CD-3"   "CD-4"   "CD-5"   "CD-6"   "CD-7"   "CD-8"   "CD-9"   "CD-10"  "CD-11"  "CD-12" 
Aggregating results
Selecting tuning parameters
Fitting mtry = 12 on full training set
[1] "Model: rf"
 [1] "clique" "CD-1"   "CD-2"   "CD-3"   "CD-4"   "CD-5"   "CD-6"   "CD-7"   "CD-8"   "CD-9"   "CD-10"  "CD-11"  "CD-12" 
Aggregating results
Selecting tuning parameters
Fitting mtry = 7 on full training set
[1] "Model: rf"
 [1] "chain" "CD-1"  "CD-2"  "CD-3"  "CD-4"  "CD-5"  "CD-6"  "CD-7"  "CD-8"  "CD-9"  "CD-10" "CD-11" "CD-12"
Aggregating results
Selecting tuning parameters
Fitting mtry = 7 on full training set
[1] "Model: rf"
 [1] "CD"    "CD-1"  "CD-2"  "CD-3"  "CD-4"  "CD-5"  "CD-6"  "CD-7"  "CD-8"  "CD-9"  "CD-10" "CD-11" "CD-12"
Aggregating results
Selecting tuning parameters
Fitting mtry = 7 on full training set
[1] "Model: rf"
 [1] "UD"    "CD-1"  "CD-2"  "CD-3"  "CD-4"  "CD-5"  "CD-6"  "CD-7"  "CD-8"  "CD-9"  "CD-10" "CD-11" "CD-12"
Aggregating results
Selecting tuning parameters
Fitting mtry = 7 on full training set
[1] "Model: rf"
 [1] "HL"    "CD-1"  "CD-2"  "CD-3"  "CD-4"  "CD-5"  "CD-6"  "CD-7"  "CD-8"  "CD-9"  "CD-10" "CD-11" "CD-12"
Aggregating results
Selecting tuning parameters
Fitting mtry = 2 on full training set
[1] "Model: rf"
 [1] "IXPD"  "CD-1"  "CD-2"  "CD-3"  "CD-4"  "CD-5"  "CD-6"  "CD-7"  "CD-8"  "CD-9"  "CD-10" "CD-11" "CD-12"
Aggregating results
Selecting tuning parameters
Fitting mtry = 2 on full training set
write.csv(rbind(confusionMatricesNB, confusionMatricesC50, confusionMatricesRF), "dev.jgit-month-cm-ALL-ALL.csv")

```{r only the best model of C5.0}
tuneGridf <- function(currentShape){
  if(currentShape=="star"){
      data.frame(trials = 10, model = "tree", winnow = TRUE)
  }
  if(currentShape=="circle"){
      data.frame(trials = 20, model = "tree", winnow = FALSE)
  }
  if(currentShape=="clique"){
      data.frame(trials = 20, model = "tree", winnow = TRUE)
  }
  if(currentShape=="chain"){
      data.frame(trials = 20, model = "tree", winnow = FALSE)
  }
  if(currentShape=="CD"){
      data.frame(trials = 20, model = "tree", winnow = FALSE)
  }
  if(currentShape=="UD"){
      data.frame(trials = 20, model = "rules", winnow = FALSE)
  }
  if(currentShape=="HL"){
      data.frame(trials = 1, model = "rules", winnow = FALSE)
  }
  if(currentShape=="IXPD"){
      data.frame(trials = 20, model = "rules", winnow = FALSE)
  }
  else{
    data.frame(trials=20, model="rules", winnow=FALSE)
  }
}
run50CV <- function(lagged, .models, .shapes, .outfilePrefix = "") {
  # Generate all combinations of targets and models to test
  experiments <- expand.grid(shape = .shapes, model = .models)
  print(experiments)
  alply(experiments, .margins = 1, function(experiment) {#aaply(array) alply(liste)
    currentShape <- paste(experiment[1, "shape"])
    currentModel <- paste(experiment[1, "model"])
     print(currentShape)
     print(currentModel)
     print(names(lagged))
    if (currentShape %in% as.list(names(lagged))) {
      # Keep only lagged columns in the dataset, plus the class
      lagged.train <- cbind(lagged[c(currentShape)],
                            lagged[grep("-", names(lagged))])
      names(lagged.train)<-as.vector(gsub("-", "", names(lagged.train)))
      print(paste("Model:", currentModel))
      print(names(lagged.train))
      # do only a single configuration
      fitControlSingle <- trainControl(method = "none")#, classProbs = TRUE)
      fit <- train(form=as.formula(paste(currentShape, "~ .")),
                   data = lagged.train,
                   method = currentModel,
                   trControl = fitControlSingle
                   # ,tuneGrid =tuneGridf(currentShape)
                    ,tuneGrid = data.frame(NumOpt=2,
                                              NumFolds=3,
                                              MinWeights=2)
                   # ,metric = "ROC"
                   )
      print(fit)
      fit
    } else {
      data.frame()
    }
  })
}


pkg.dataset.nzv.binary <- as.data.frame(cbind(pkg.dataset.nzv[c("star","circle","clique","chain","CD","UD","HL","IXPD")],
                                              ifelse(pkg.dataset.nzv[grep("-", names(pkg.dataset.nzv))]<1,0,1)))
# modelLookup("C5.0")
# models <- c("C5.0") # "C5.0" "logreg" has some issues, should be tested outside
# set.seed(825)
# trainC50 <- run50CV(pkg.dataset.nzv.binary, models, targets, "tomcat-")

# library(rJava)
modelLookup("JRip")
models <- c("JRip")
set.seed(825)
trainjrip <- run50CV(pkg.dataset.nzv.binary, models, targets, "dev.jgit-")
# write.csv(pkg.dataset.nzv.binary, "tomcat-cm-lagged-week.csv")


c50.1 <- trainjrip$`1`$finalModel #start
c50.2 <- trainjrip$`2`$finalModel #circle
c50.3 <- trainjrip$`4`$finalModel #clique
c50.4 <- trainjrip$`5`$finalModel #chain
c50.5 <- trainjrip$`6`$finalModel #cd
c50.6 <- trainjrip$`7`$finalModel #ud
c50.7 <- trainjrip$`8`$finalModel #hl
c50.8 <- trainjrip$`9`$finalModel #ixpd
write(as.character(summary(c50.1)),"data/rule/dev.jgit-jrip-month-c50.star.txt")
write(as.matrix(scan(text=.jcall(c50.1$classifier, "S", "toString") ,sep="\n", what="") )[
    -c(1:2, 6), ,drop=FALSE],"data/rule/dev.jgit-jrip-month-c50.star.txt",append=TRUE)
write(as.character(summary(c50.2)),"data/rule/dev.jgit-jrip-month-c50.circle.txt")
write(as.matrix(scan(text=.jcall(c50.2$classifier, "S", "toString") ,sep="\n", what="") )[
    -c(1:2, 6), ,drop=FALSE],"data/rule/dev.jgit-jrip-month-c50.circle.txt",append=TRUE)
write(as.character(summary(c50.3)),"data/rule/dev.jgit-jrip-month-c50.clique.txt")
write(as.matrix(scan(text=.jcall(c50.3$classifier, "S", "toString") ,sep="\n", what="") )[
    -c(1:2, 6), ,drop=FALSE],"data/rule/dev.jgit-jrip-month-c50.clique.txt",append=TRUE)
write(as.character(summary(c50.4)),"data/rule/dev.jgit-jrip-month-c50.chain.txt")
write(as.matrix(scan(text=.jcall(c50.4$classifier, "S", "toString") ,sep="\n", what="") )[
    -c(1:2, 6), ,drop=FALSE],"data/rule/dev.jgit-jrip-month-c50.chain.txt",append=TRUE)
write(as.character(summary(c50.5)),"data/rule/dev.jgit-jrip-month-c50.cd.txt")
write(as.matrix(scan(text=.jcall(c50.5$classifier, "S", "toString") ,sep="\n", what="") )[
    -c(1:2, 6), ,drop=FALSE],"data/rule/dev.jgit-jrip-month-c50.cd.txt",append=TRUE)
write(as.character(summary(c50.6)),"data/rule/dev.jgit-jrip-month-c50.ud.txt")
write(as.matrix(scan(text=.jcall(c50.6$classifier, "S", "toString") ,sep="\n", what="") )[
    -c(1:2, 6), ,drop=FALSE],"data/rule/dev.jgit-jrip-month-c50.ud.txt",append=TRUE)
write(as.character(summary(c50.7)),"data/rule/dev.jgit-jrip-month-c50.hl.txt")
write(as.matrix(scan(text=.jcall(c50.7$classifier, "S", "toString") ,sep="\n", what="") )[
    -c(1:2, 6), ,drop=FALSE],"data/rule/dev.jgit-jrip-month-c50.hl.txt",append=TRUE)
write(as.character(summary(c50.8)),"data/rule/dev.jgit-jrip-month-c50.ixpd.txt")
write(as.matrix(scan(text=.jcall(c50.8$classifier, "S", "toString") ,sep="\n", what="") )[
    -c(1:2, 6), ,drop=FALSE],"data/rule/dev.jgit-jrip-month-c50.ixpd.txt",append=TRUE)
```

```{r read all confusion matrices}

# library(plyr)
# library(stringr)
files <- list.files(path = "data/ml-results/jgit/month", pattern = ".csv")
# temp <- lapply(files, read.csv,header=TRUE,sep=",")
readFromCsv <- function(filename, header=TRUE, sep=","){
    ret <- read.csv(paste0("data/ml-results/jgit/month/",filename),header,sep)
    appo <- str_split_fixed(filename, "\\-",4)
    ret$System <- appo[,1]
    # ret$System <- appo[,2]
    ret$Var <- appo[,3]
    ret$Model <- gsub(".csv","",appo[,4])
    ret$File <- filename #EDIT
    ret
}
temp <- ldply(as.list(files), readFromCsv)
write.csv(file = "all-md-ml.csv",temp)
```


```{r only the best model of C5.0 smote}
tuneGridf <- function(currentShape){
  if(currentShape=="star"){
      data.frame(trials = 20, model = "tree", winnow = TRUE)
  }
  if(currentShape=="circle"){
      data.frame(trials = 20, model = "tree", winnow = TRUE)
  }
  if(currentShape=="clique"){
      data.frame(trials = 20, model = "tree", winnow = TRUE)
  }
  if(currentShape=="chain"){
      data.frame(trials = 20, model = "tree", winnow = TRUE)
  }
  if(currentShape=="CD"){
      data.frame(trials = 20, model = "tree", winnow = FALSE)
  }
  if(currentShape=="UD"){
      data.frame(trials = 20, model = "rules", winnow = FALSE)
  }
  if(currentShape=="HL"){
      data.frame(trials = 20, model = "rules", winnow = FALSE)
  }
  if(currentShape=="IXPD"){
      data.frame(trials = 20, model = "tree", winnow = FALSE)
  }
  else{
    data.frame(trials=20, model="rules", winnow=FALSE)
  }
}
run50CV <- function(lagged, .models, .shapes, .outfilePrefix = "") {
  # Generate all combinations of targets and models to test
  experiments <- expand.grid(shape = .shapes, model = .models)
  print(experiments)
  alply(experiments, .margins = 1, function(experiment) {#aaply(array) alply(liste)
    currentShape <- paste(experiment[1, "shape"])
    currentModel <- paste(experiment[1, "model"])
     print(currentShape)
     print(currentModel)
     print(names(lagged))
    if (currentShape %in% as.list(names(lagged))) {
      # Keep only lagged columns in the dataset, plus the class
      lagged.train <- cbind(lagged[c(currentShape)],
                            lagged[grep("-", names(lagged))])
      names(lagged.train)<-as.vector(gsub("-", "", names(lagged.train)))
      print(paste("Model:", currentModel))
      print(names(lagged.train))
      # do only a single configuration
      fitControlSingle <- trainControl(method = "none")#, classProbs = TRUE)
      fit <- train(form=as.formula(paste(currentShape, "~ .")),
                   data = lagged.train,
                   method = currentModel,
                   trControl = fitControlSingle
                   #,tuneGrid = tuneGridf(currentShape)
                   ,tuneGrid = data.frame(NumOpt=2, NumFolds=3, MinWeights=2)
                   # ,metric = "ROC"
                   )
      print(fit)
      fit
    } else {
      data.frame()
    }
  })
}


pkg.dataset.nzv.binary <- as.data.frame(cbind(pkg.dataset.nzv[c("star","circle","clique","chain","CD","UD","HL","IXPD")],
                                              ifelse(pkg.dataset.nzv[grep("-", names(pkg.dataset.nzv))]<1,0,1)))
# modelLookup("C5.0")
# models <- c("C5.0") # "C5.0" "logreg" has some issues, should be tested outside
# set.seed(825)
# trainC50 <- run50CV(pkg.dataset.nzv.binary, models, targets, "tomcat-")

# library(rJava)
modelLookup("JRip")
models <- c("JRip")
set.seed(825)
trainjrip <- run50CV(pkg.dataset.nzv.binary, models, targets, "dev.jgit-")
# write.csv(pkg.dataset.nzv.binary, "tomcat-cm-lagged-week.csv")


c50.1 <- trainjrip$`1`$finalModel #star
c50.2 <- trainjrip$`2`$finalModel #circle
c50.3 <- trainjrip$`4`$finalModel #clique
c50.4 <- trainjrip$`5`$finalModel #chain
c50.5 <- trainjrip$`6`$finalModel #cd
c50.6 <- trainjrip$`7`$finalModel #ud
c50.7 <- trainjrip$`8`$finalModel #hl
c50.8 <- trainjrip$`9`$finalModel #ixpd
write(as.character(summary(c50.1)),"data/rule.smote/dev.jgit-jrip-month-c50.star.txt")
write(as.matrix(scan(text=.jcall(c50.1$classifier, "S", "toString") ,sep="\n", what="") )[
    -c(1:2, 6), ,drop=FALSE],"data/rule.smote/dev.jgit-jrip-month-c50.star.txt",append=TRUE)
write(as.character(summary(c50.2)),"data/rule.smote/dev.jgit-jrip-month-c50.circle.txt")
write(as.matrix(scan(text=.jcall(c50.2$classifier, "S", "toString") ,sep="\n", what="") )[
    -c(1:2, 6), ,drop=FALSE],"data/rule.smote/dev.jgit-jrip-month-c50.circle.txt",append=TRUE)
write(as.character(summary(c50.3)),"data/rule.smote/dev.jgit-jrip-month-c50.clique.txt")
write(as.matrix(scan(text=.jcall(c50.3$classifier, "S", "toString") ,sep="\n", what="") )[
    -c(1:2, 6), ,drop=FALSE],"data/rule.smote/dev.jgit-jrip-month-c50.clique.txt",append=TRUE)
write(as.character(summary(c50.4)),"data/rule.smote/dev.jgit-jrip-month-c50.chain.txt")
write(as.matrix(scan(text=.jcall(c50.4$classifier, "S", "toString") ,sep="\n", what="") )[
    -c(1:2, 6), ,drop=FALSE],"data/rule.smote/dev.jgit-jrip-month-c50.chain.txt",append=TRUE)
write(as.character(summary(c50.5)),"data/rule.smote/dev.jgit-jrip-month-c50.cd.txt")
write(as.matrix(scan(text=.jcall(c50.5$classifier, "S", "toString") ,sep="\n", what="") )[
    -c(1:2, 6), ,drop=FALSE],"data/rule.smote/dev.jgit-jrip-month-c50.cd.txt",append=TRUE)
write(as.character(summary(c50.6)),"data/rule.smote/dev.jgit-jrip-month-c50.ud.txt")
write(as.matrix(scan(text=.jcall(c50.6$classifier, "S", "toString") ,sep="\n", what="") )[
    -c(1:2, 6), ,drop=FALSE],"data/rule.smote/dev.jgit-jrip-month-c50.ud.txt",append=TRUE)
write(as.character(summary(c50.7)),"data/rule.smote/dev.jgit-jrip-month-c50.hl.txt")
write(as.matrix(scan(text=.jcall(c50.7$classifier, "S", "toString") ,sep="\n", what="") )[
    -c(1:2, 6), ,drop=FALSE],"data/rule.smote/dev.jgit-jrip-month-c50.hl.txt",append=TRUE)
write(as.character(summary(c50.8)),"data/rule.smote/dev.jgit-jrip-month-c50.ixpd.txt")
write(as.matrix(scan(text=.jcall(c50.8$classifier, "S", "toString") ,sep="\n", what="") )[
    -c(1:2, 6), ,drop=FALSE],"data/rule.smote/dev.jgit-jrip-month-c50.ixpd.txt",append=TRUE)
```


